### 2016-10-19 Paper.tex
first commit

% Template for ISBI-2016 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{Deep Neural Network for Nuclei Segmentation in Histopathology images}
%
% Single address.
% ---------------
%%% Not too sure about who to thank, I guess me, you, phil, and ema?
\name{Peter Naylor, Thomas Walter, J.P. Vert and E. Barillot\thanks{Thanks to XYZ agency for funding.}}
\address{Insitute Curie/ Mines paristech Inserm}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
% More than two addresses
% -----------------------
% \name{Author Name$^{\star \dagger}$ \qquad Author Name$^{\star}$ \qquad Author Name$^{\dagger}$}
%
% \address{$^{\star}$ Affiliation Number One \\
%     $^{\dagger}$}Affiliation Number Two
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
The abstract should appear at the top of the left-hand column of text, about
0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
beginning of the main text.  The abstract should contain about 100 to 150
words, and should be identical to the abstract text submitted electronically
along with the paper cover sheet.  All manuscripts must be in English, printed
in black ink.
\end{abstract}
%
\begin{keywords}
Deep Networks, Nuclei Segmentation, Histpathology. Maybe more?
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

These guidelines include complete descriptions of the fonts, spacing, and
related information for producing your proceedings manuscripts.

\section{Related work}
\label{sec:related}

Talk about related work.
Recent work in deep learning for segmentation, histopathology analysis helped by images. Maybe not too much as the paper is small..
\section{DataSet}
\label{sec:dataset}
Creating of the data set, some features about it. ITK-snap, some statistics about it.
\section{Methodology}
\label{sec:method}
About different architectures described. Validation scheme.

\section{Result}
\label{sec:result}
table of values
\section{Discussion}
\label{sec:discussion}
What's next?

\section{Formatting your paper}
\label{sec:format}

All printed material, including text, illustrations, and charts, must be kept
within a print area of 7 inches (178 mm) wide by 9 inches (229 mm) high. Do
not write or print anything outside the print area. The top margin must be 1
inch (25 mm), except for the title page, and the left margin must be 0.75 inch
(19 mm).  All {\it text} must be in a two-column format. Columns are to be 3.39
inches (86 mm) wide, with a 0.24 inch (6 mm) space between them. Text must be
fully justified.

\section{PAGE TITLE SECTION}
\label{sec:pagestyle}

The paper title (on the first page) should begin 1.38 inches (35 mm) from the
top edge of the page, centered, completely capitalized, and in Times 14-point,
boldface type.  The authors' name(s) and affiliation(s) appear below the title
in capital and lower case letters.  Papers with multiple authors and
affiliations may require two or more lines for this information.

\section{TYPE-STYLE AND FONTS}
\label{sec:typestyle}

To achieve the best rendering both in the proceedings and from the CD-ROM, we
strongly encourage you to use Times-Roman font.  In addition, this will give
the proceedings a more uniform look.  Use a font that is no smaller than nine
point type throughout the paper, including figure captions.

In nine point type font, capital letters are 2 mm high.  If you use the
smallest point size, there should be no more than 3.2 lines/cm (8 lines/inch)
vertically.  This is a minimum spacing; 2.75 lines/cm (7 lines/inch) will make
the paper much more readable.  Larger type sizes require correspondingly larger
vertical spacing.  Please do not double-space your paper.  True-Type 1 fonts
are preferred.

The first paragraph in each section should not be indented, but all the
following paragraphs within the section should be indented as these paragraphs
demonstrate.

\section{MAJOR HEADINGS}
\label{sec:majhead}

Major headings, for example, "1. Introduction", should appear in all capital
letters, bold face if possible, centered in the column, with one blank line
before, and one blank line after. Use a period (".") after the heading number,
not a colon.

\subsection{Subheadings}
\label{ssec:subhead}

Subheadings should appear in lower case (initial word capitalized) in
boldface.  They should start at the left margin on a separate line.

\subsubsection{Sub-subheadings}
\label{sssec:subsubhead}

Sub-subheadings, as in this paragraph, are discouraged. However, if you
must use them, they should appear in lower case (initial word
capitalized) and start at the left margin on a separate line, with paragraph
text beginning on the following line.  They should be in italics.

\section{PRINTING YOUR PAPER}
\label{sec:print}

Print your properly formatted text on high-quality, 8.5 x 11-inch white printer
paper. A4 paper is also acceptable, but please leave the extra 0.5 inch (12 mm)
empty at the BOTTOM of the page and follow the top and left margins as
specified.  If the last page of your paper is only partially filled, arrange
the columns so that they are evenly balanced if possible, rather than having
one long column.

In \LaTeX, to start a new column (but not a new page) and help balance the
last-page column lengths, you can use the command ``$\backslash$pagebreak'' as
demonstrated on this page (see the \LaTeX\ source below).

\section{PAGE NUMBERING}
\label{sec:page}

Please do {\bf not} paginate your paper.  Page numbers, session numbers, and
conference identification will be inserted when the paper is included in the
proceedings.

\section{ILLUSTRATIONS, GRAPHS, AND PHOTOGRAPHS}
\label{sec:illust}

Illustrations must appear within the designated margins.  They may span the two
columns.  If possible, position illustrations at the top of columns, rather
than in the middle or at the bottom.  Caption and number every illustration.
All halftone illustrations must be clear black and white prints.  If you use
color, make sure that the color figures are clear when printed on a black-only
printer.

Since there are many ways, often incompatible, of including images (e.g., with
experimental results) in a \LaTeX\ document, below is an example of how to do
this \cite{Lamp86}.

% Below is an example of how to insert images. Delete the ``\vspace'' line,
% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
% with a suitable PostScript file name.
% -------------------------------------------------------------------------
\begin{figure}[htb]

\begin{minipage}[b]{1.0\linewidth}
  \centering
  \centerline{\includegraphics[width=8.5cm]{image1}}
%  \vspace{2.0cm}
  \centerline{(a) Result 1}\medskip
\end{minipage}
%
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{image2}}
%  \vspace{1.5cm}
  \centerline{(b) Results 3}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{image3}}
%  \vspace{1.5cm}
  \centerline{(c) Result 4}\medskip
\end{minipage}
%
\caption{Example of placing a figure with experimental results.}
\label{fig:res}
%
\end{figure}

% To start a new column (but not a new page) and help balance the last-page
% column length use \vfill\pagebreak.
% -------------------------------------------------------------------------
\vfill
\pagebreak

\section{FOOTNOTES}
\label{sec:foot}

Use footnotes sparingly (or not at all!) and place them at the bottom of the
column on the page on which they are referenced. Use Times 9-point type,
single-spaced. To help your readers, avoid using footnotes altogether and
include necessary peripheral observations in the text (within parentheses, if
you prefer, as in this sentence).

\section{COPYRIGHT FORMS}
\label{sec:copyright}

You must include your fully completed, signed IEEE copyright release form when
you submit your paper. We {\bf must} have this form before your paper can be
published in the proceedings.  The copyright form is available as a Word file,
a PDF file, and an HTML file. You can also use the form sent with your author
kit.

\section{REFERENCES}
\label{sec:ref}

List and number all bibliographical references at the end of the paper.  The references can be numbered in alphabetic order or in order of appearance in the document.  When referring to them in the text, type the corresponding reference number in square brackets as shown at the end of this sentence \cite{C2}.

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{strings,refs}

\end{document}

### 2016-11-04 Paper.tex
first update

@@
 \usepackage{spconf,amsmath,graphicx}
-
+\usepackage{amsfonts}
 % Example definitions.
@@
 \label{sec:dataset}
-Creating of the data set, some features about it. ITK-snap, some statistics about it.
+
+%% Contribution as a dataset, small introduction
+One of the main contributions of this paper is the now public available 
+nuclei detection dataset within HE stainned histopathology images which 
+can be found at www.cbio.ensmp.fr:/pnaylor/download/dataset.zip (not 
+a true address). This annotated dataset provides images clustered by 
+patients. Each patient has at least 3 annotated $512 \times 512$ HE 
+stainned histopathology images with their associated ground truth. Each 
+ground truth image is a $512 \times 512$ where each pixel value above 
+$0$ is considered as a pixel belonging to a nuclei. The differences in 
+values of these pixels denote different nucleus, such an annotation can 
+be used in several processing step which does or doesn't take into 
+account clutered nuclei. See figure \ref{fig:annotation} for an example of 
+three annotated images. This annotation was conducted via the help of 
+the software ITK-snap and were annotated by the authors of the paper.
+
+%% Data set creation procedure
+These patients were randomly picked from an unpublished study on
+tripple negative breast cancer. For each of these patients we had access
+to their biopsy sample as a whole slide image (WSI). WSI enables a
+medical practitionner to digitize the huge amount of information that
+can be found in glass slides. WSI can be up to 60 GB big
+uncompressed and can't be stored in RAM on a standard computer. Given
+the WSI of a patient, we randomly cropped $512 \times 512$ samples 
+from the WSI. %% explain that we choose the tissue area? 
+3 to 7 images were choosen from the randomly sampled images to try and give the most diversed dataset among these patients.
+Once the samples were choosen, we fully annotated each nuclei via the software ITK-snap and touching nuclei are differentiate via a different annotation value.
+
+%%Data set description 
+We can describe the dataset provided.
+
 \section{Methodology}
 \label{sec:method}
-About different architectures described. Validation scheme.
+%% Segmentation task
+Let A be the space of RGB images, A can typically be 
+$\mathbb{R}^{n \times p \times 3}$ and let B the space B the space of annotation 
+images, in our case $\{0,1\}^{n \times p}$. We have a set of 
+$(A_l,B_l)_{l \in [1, N]}$ for a supervised learning approach. Our goal is 
+a prediction task 
+named as semantic segmentation, we wish to maximize the prediction of 
+an unseen element belonging to B given an new element in A. We maximize 
+thus prediction by modelizing our prediction function as the softmax output of a deep neural 
+network. We find the model parameters by minimizing a log loss function 
+defined as:
+ $\frac{1}{\sum_{i,j}w_{ij}} \sum_{i,j} \sum_k w_{i,j} t_{i,j,k} \log (\widehat{p_{i,j,k}})$
+, where $k$ designates a certain label, $w_{i,j}$ is 
+certain weight given to pixel $i,j$, $t_{i,j,k}$ is equal to 1 if pixel $i,j$ is 
+of class $k$ and $\widehat{p_{i,j,k}}$ designates the estimated probability 
+of pixel $i,j$ of being $k$ via the softmax output of the neural network.
+We minimize the loss function via stochastic gradient descent.
 
+%% Validation scheme
+We have our training set $(A_l,B_l)_{l \in [1, N]}$ where N is equal to 
+34, how ever each element $A_l$ belongs to a certain patients and 
+several elements $A_l$ can belong to the same patient. As we are 
+dealing with histopathology images, it is know that samples can widely 
+vary from one patient to the other. We thus validate our model by a 
+leave one patient out scheme. Our validation scheme is as followed, for a 
+given set of hype parameters, we 
+train our model on every patient except one that is used for validation. 
+Our final score is averaged over all patients.
+Several metrics assess the quality of the model, the accuracy (Acc), the 
+F1 score and a performance (Perf) score which is the mean between the 
+true positive rates and the true negative rates.
+
+%% Data augmentation and Hyper parameter training: Training scheme
+%% Check number of images and number of transformations
+To train our models, as the number of available annotated is scarse, we 
+used a great number of transformation for the data augmentation. From 
+a original size of 33 annotated images, adding flips, rotations, bluriness 
+and random elastic deformations enabled us to have more then 
+$400 000$ training images per patient. 
+We also try out several hyperparameter configurations: the learning rate and 
+momentum for the stochastic gradient descent, the weight decay value.  
+In practice, we found that hyperparameters tuning didn't influence the 
+scores much, the exepction being the learning rate. If the learning rate 
+was not of the right magnitude the given network did not seem to learn. 
+We also experienced with different 
+initialization value and if possible, we also considered pretrained layers. 
+Using pretrained layers made learning more efficient and made score 
+values more robust.
+
+\section{Different architectures/Results}
+\label{sec:method}
+We experience with 4 know arhitectures in semantic segmentation, one 
+will be named BaochuanNet, Fully Convolutionnal Net (FCN), DeconvNet, 
+UNet. The most basic architecture, BaochuanNet, consists of 4 
+convolutionnal layer where each convolutionnal layer has 8 feature map. 
+This net, being not deep, has the advantage of being less 
+computationnally intensive. FCN is a first attempt of applying "deep 
+feature" representations to the task of semantic segmentation. This 
+archicture has the advantage of re-using a classical deep learning 
+architecture with added on upsampling layer and skip layers. The 
+upsampling layers enable the network to learn a pixel level classification 
+and the skip layers enable the network to fuse different levels of 
+abstraction to the final prediction. This model can be fine tuned with a 
+set of pretrained-weights extracted from the classical deep learning 
+architecture. DeconvNet is also based on a classical architecture, 
+however, in this network their are no skip layer as one intends to learn 
+the proper upsampling threw repeated deconvolution and convolution 
+layers. This model can also be fine tuned.
 \section{Result}
@@
   \centering
-  \centerline{\includegraphics[width=8.5cm]{image1}}
+  \centerline{\includegraphics[width=8.5cm]{RGB_1}}
 %  \vspace{2.0cm}
-  \centerline{(a) Result 1}\medskip
+  \centerline{Patient 498959}\medskip
 \end{minipage}
@@
   \centering
-  \centerline{\includegraphics[width=4.0cm]{image2}}
+  \centerline{\includegraphics[width=4.0cm]{RGB_1}}
 %  \vspace{1.5cm}
-  \centerline{(b) Results 3}\medskip
+  \centerline{Sample from patient 498959}\medskip
 \end{minipage}
@@
   \centering
-  \centerline{\includegraphics[width=4.0cm]{image3}}
+  \centerline{\includegraphics[width=4.0cm]{GT_1}}
 %  \vspace{1.5cm}
-  \centerline{(c) Result 4}\medskip
+  \centerline{Associated ground truth}\medskip
 \end{minipage}
 %
-\caption{Example of placing a figure with experimental results.}
-\label{fig:res}
+%
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{RGB_2}}
+%  \vspace{1.5cm}
+  \centerline{Sample from patient 581910}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{GT_2}}
+%  \vspace{1.5cm}
+  \centerline{Associated ground truth}\medskip
+\end{minipage}
+%
+%
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{RGB_3}}
+%  \vspace{1.5cm}
+  \centerline{Sample from patient 581910}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{GT_3}}
+%  \vspace{1.5cm}
+  \centerline{Associated ground truth}\medskip
+\end{minipage}
+%
+\caption{Random annotated samples from the dataset}
+\label{fig:annotation}
 %

### 2016-11-06 Paper.tex
Introduction nearly ready

@@
 \usepackage{amsfonts}
+\usepackage[utf8]{inputenc}
+\usepackage[francais]{babel}
+
 % Example definitions.
@@
 % ------
-\title{Deep Neural Network for Nuclei Segmentation in Histopathology images}
+\title{Nuclei Segmentation in Histopathology
+  images using Deep Neural Networks}
 %
@@
 %%% Not too sure about who to thank, I guess me, you, phil, and ema?
-\name{Peter Naylor, Thomas Walter, J.P. Vert and E. Barillot\thanks{Thanks to XYZ agency for funding.}}
-\address{Insitute Curie/ Mines paristech Inserm}
+%\name{Peter Naylor, Marick Lae, Fabien Reyal and Thomas Walter\thanks{}}
+%\address{(1)   MINES ParisTech, PSL Research University, CBIO - Centre de bio-informatique, 35 rue St Honoré 77300 Fontainebleau, France
+%(2)   Institut Curie, 75248 Paris Cedex, France
+%(3)   INSERM U900, 75248 Paris Cedex, France}
 %
@@
 % -----------------------
-% \name{Author Name$^{\star \dagger}$ \qquad Author Name$^{\star}$ \qquad Author Name$^{\dagger}$}
-%
-% \address{$^{\star}$ Affiliation Number One \\
-%     $^{\dagger}$}Affiliation Number Two
+
+\name{Peter Naylor$^{1,2,3}$\sthanks{Peter Naylor has received a PhD
+  fellowship from the Ligue contre le Cancer. } \qquad Marick Lae$^{2}$
+  \qquad Fabien Reyal$^{2}$\qquad Thomas Walter$^{1,2,3}$}
+
+\address{$^{1}$MINES ParisTech, PSL Research University, CBIO - Centre
+  de Bioinformatique,\\ 
+  35 rue St Honoré 77300 Fontainebleau, France \\
+$^{2}$Institut Curie, 75248 Paris Cedex, France\\
+$^{3}$INSERM U900, 75248 Paris Cedex, France}
 %
@@
 \begin{abstract}
-The abstract should appear at the top of the left-hand column of text, about
-0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
-length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
-beginning of the main text.  The abstract should contain about 100 to 150
-words, and should be identical to the abstract text submitted electronically
-along with the paper cover sheet.  All manuscripts must be in English, printed
-in black ink.
+%The abstract should appear at the top of the left-hand column of text, about
+%0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
+%length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
+%beginning of the main text.  The abstract should contain about 100 to 150
+%words, and should be identical to the abstract text submitted electronically
+%along with the paper cover sheet.  All manuscripts must be in English, printed
+%in black ink.
 \end{abstract}
@@
 \begin{keywords}
-Deep Networks, Nuclei Segmentation, Histpathology. Maybe more?
+Deep Learnnig, Convolutional Neural Networks, Nuclei Segmentation,
+Histpathology, Digital Pathology, Breast Cancer, Cellular Phenotyping
 \end{keywords}
@@
 
-These guidelines include complete descriptions of the fonts, spacing, and
-related information for producing your proceedings manuscripts.
+% images in cancer research, histopathology --> digital pathology
+Today, large sequencing approaches build the main body of cancer
+research programs and they have revolutionized our understanding of
+the molecular basis of cancer. In clinical practice however,
+molecular profiling is paralleled with the more traditional
+(and mostly manual) analysis of stained histological tumor
+sections. With the avent of digital pathology, i.e. the scanning and
+digital storage of diseased tissue sections, it is now possible to
+build tools for the quantitative and automatic analysis of these
+complex and informative image data. Indeed, this is a very promising
+approach for several reasons: image based approaches
+provide us with spatial information that is absent in genomic,
+transcriptomic and epigenetic studies of cancer. In addition they
+allow analysis of individual cells, such that it is possible to study
+cellular heterogeneity. Cellular heterogeneity has been acknowledged
+to be of major importance in cancer research and treatment. Also, it
+is possible to analyze cells in terms of morphology and phenotype,
+which brings in a complementary piece of functionally relevant
+information.
+
+% two approaches: CAD vs. understanding
+For these reasons, analysis of histopathology data has received much
+attention over the last years. Most of these works are in the frame of
+Computer Aided Diagnosis (CAD) and aim at automatically performing the
+task of a human pathologist or at assisting in the diagnosis. For such
+a task, the nature of the features according to which a certain
+classification or detection task is solved is mostly
+irrelevant. A conceptually different approach is to derive biologically
+relevant features, such as phenotype distributions, spatial cell type
+distributions or heterogeneity measures from the tissue data in order to reach some
+understanding as of which biological features can be predictive for
+clinical variables such as resistance to treatment or relapse
+probability.
+
+% segmentation is the bottleneck of cellular phenotyping in cancer
+% tissues. 
+In this latter case, one of the essential steps is to
+segment nuclei from tissue images in order to be able to
+assign them a cell type or phenotypic label and to evaluate their
+spatial distribution. We concentrate on nuclei, as they are indicative
+of many cellular phenotypes\citep{Chow2012}, and their morphology is 
+currently used by pathologists in order to
+identify the mitotic index and the level of nuclear pleomorphism
+
+Regarding cellular phenotyping, we will focus on nuclear morphologies,
+because (1) nuclei are indicative of many cellular phenotypes20, (2)
+their morphology is currently used by pathologists in order to
+identify the mitotic index and the level of nuclear pleomorphism12 and
+(3) their segmentation is feasible5 in contrast to many other cellular
+structures, such as the plasma membrane for instance.
+
+Yet, segmentation of nuclei is a
+complicated task: tissue type, staining differences and cell type
+convey them different visual characteristics, which makes it very difficult to
+design traditional image segmentation algorithms that work
+satisfactorily for all of these different cases. On the other hand,
+deep learning algorithms have been recently used
+
+% motivation of the deep learning approach (for instance by taking
+% fewer samples). t
+
+of bioinformatics programs aiming at
+
+related to cancer and they
+have revolutionized our understanding of the molecular basis of cancer
+and led to the definition of clinically relevant subtypes, bearing
+high potential for the development of new cancer therapies.
 

### 2016-11-06 Paper.tex
last day

--- 2016-11-04 Paper.tex
@@
 \label{sec:related}
+Image segmentation and object recognition in medical imagining have 
+been tackled for many years and many approaches have been found. 
+Methods based on mathematical morphological operators have been 
+widely used and applied for segmentation and feature extraction, 
+however such methods rely on the user to manually define the 
+information that is relevant for his task \cite{irshad2014methods}. 
+Segmentation methods based on a strong priori information are also 
+possible and yield comparable results in terms of accuracy, in 
+\cite{ranefall2016fast} they segment the picture using a ellispe fit 
+which is considerably faster than other state of the art methods. Graph-
+based tools for segmentation are also possible in histopathology 
+\cite{ta2009graph}. \cite{manivannanlocal} focus on gland 
+segmentation, they achieve good results by predicting image patches as 
+a whole, via a classification scheme. The output confidence vector is 
+then preprocessed to obtain the final segmentation. Alternative methods 
+have arisen from the achieving Convolutional neural networks 
+\cite{lecun}, in particular strong incentive rose with the very impressive 
+results that they achieved in the pascal voc challenge with 
+\cite{ImageNet}. Recent advances in deep neural network, and in 
+particular in their optimization have made them become the state-of-the-
+art model for object recognition.  Deep neural network have also been 
+used for different task and have yielded very impressiv results, we can think of 
+semantic segmentation problems, where \cite{long2015fcn} use "de-
+convolution layers" and up-sampling in order to identify and precisely 
+locate objects within a picture. Different architecture arising from 
+different intuition are also possible and have been applied in this paper
+Talk about related work.
 
-Talk about related work.
-Recent work in deep learning for segmentation, histopathology analysis helped by images. Maybe not too much as the paper is small..
 \section{DataSet}
@@
 nuclei detection dataset within HE stainned histopathology images which 
-can be found at www.cbio.ensmp.fr:/pnaylor/download/dataset.zip (not 
-a true address). This annotated dataset provides images clustered by 
+can be found at website %\url{www.cbio.ensmp.fr:/pnaylor/download/dataset.zip} 
+(not a true address). This annotated dataset provides images clustered by 
 patients. Each patient has at least 3 annotated $512 \times 512$ HE 
@@
 %%Data set description 
-We can describe the dataset provided.
+In this data set we have annotated a considerous amount of cells, 
+including normal breast cells (epithelial and lobule cells),  cancerous 
+breast cells, fibroblasts,  endothelial cells, fat cells, macrophage cells and 
+inflammatory cells (lymphocytes and plasmocytes). For the moment, cell types have not been seperated, which means that in this dataset every annotation corresponds to a global type of cell.
+
+\begin{itemize}
+\item Number of images: 33 \\
+\item Number  of cells: 2754 \\
+\item Maximum number of cells in one sample: 293 \\
+\item Minimum number of cells in one sample: 5 \\
+\item Mean number of cells: 83 \\
+\item Standard deviation of number of cells: 63 \\
+\end{itemize}
 
@@
 and random elastic deformations enabled us to have more then 
-$400 000$ training images per patient. 
+$400 000$ training images. 
 We also try out several hyperparameter configurations: the learning rate and 
@@
 \label{sec:method}
-We experience with 4 know arhitectures in semantic segmentation, one 
+We experience with 4 known arhitectures in semantic segmentation, one 
 will be named BaochuanNet, Fully Convolutionnal Net (FCN), DeconvNet, 
@@
 the proper upsampling threw repeated deconvolution and convolution 
-layers. This model can also be fine tuned.
+layers.
+This model can also be fine tuned.
+The final architecture that we tried is the UNet.
+This network combines both contribution of the above networks, the UNet has a similar architecture to the DeconvNet with skip layers.
 \section{Result}
 \label{sec:result}
-table of values
+
+\begin{tabular}{|c|c|c|c|c|c|}
+ & UNet & Baochuan & DeconvNet & FCN & Ensemble \\
+%\hrule
+Accuracy          &       0.89 &       0.94 & 0.97\\
+IU   &       0.70 &       0.76 &     0.86 \\
+Recall                     &       0.75 &       0.74  &     0.86 &&\\
+Precision                  &       0.64 &       0.74 &     0.86 &&\\
+F1                         &       0.69 &       0.74 &     0.86 &&  \\
+TP             &       0.75 &       0.74 &     0.86 && \\
+TN             &       0.92 &       0.96 &     0.98 &&\\
+Performance                &       0.84 &       0.85 &     0.92 &&\\
+Pixel error                &       0.11 &       0.06 &     0.03 &&\\
+\end{tabular}
+
 \section{Discussion}

### 2016-11-06 Paper.tex
Introduction is finished

--- 2016-11-06 Paper.tex
@@
 \usepackage[francais]{babel}
+\usepackage{hyperref}
 
@@
 spatial distribution. We concentrate on nuclei, as they are indicative
-of many cellular phenotypes\citep{Chow2012}, and their morphology is 
+of many cellular phenotypes\cite{Chow2012}, and their morphology is 
 currently used by pathologists in order to
-identify the mitotic index and the level of nuclear pleomorphism
-
-Regarding cellular phenotyping, we will focus on nuclear morphologies,
-because (1) nuclei are indicative of many cellular phenotypes20, (2)
-their morphology is currently used by pathologists in order to
-identify the mitotic index and the level of nuclear pleomorphism12 and
-(3) their segmentation is feasible5 in contrast to many other cellular
-structures, such as the plasma membrane for instance.
+identify the mitotic index and the level of nuclear
+pleomorphism\cite{Elston1991}.
 
@@
 satisfactorily for all of these different cases. On the other hand,
-deep learning algorithms have been recently used
+deep learning algorithms have been used recently with great success to
+complex segmentation tasks in biology\cite{Ciresan2012,Ronneberger2015}.
 
-% motivation of the deep learning approach (for instance by taking
-% fewer samples). t
-
-of bioinformatics programs aiming at
-
-related to cancer and they
-have revolutionized our understanding of the molecular basis of cancer
-and led to the definition of clinically relevant subtypes, bearing
-high potential for the development of new cancer therapies.
+The contribution of this paper is three-fold: (1) we have generated a
+ground truth of annotated images containing segmentation results for
+more than 2000 cells. The dataset can be used by the scientific
+community. (2) We apply a deep neural network end-to-end strategy and
+demonstrate the superiority of this approach with respect to
+previously proposed simpler architectures. (3) We propose a
+post-processing strategy of the posterior probabilities provided by
+the network. This post-processing strategy is based on mathematical
+morphology and has a rigorous interpretation as to when objects are to
+be split.
 
@@
 \bibliographystyle{IEEEbib}
-\bibliography{strings,refs}
+\bibliography{strings}
 

### 2016-11-07 Paper.tex
small adds

--- 2016-11-06 Paper.tex
@@
 
-\section{Formatting your paper}
-\label{sec:format}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area of 7 inches (178 mm) wide by 9 inches (229 mm) high. Do
-not write or print anything outside the print area. The top margin must be 1
-inch (25 mm), except for the title page, and the left margin must be 0.75 inch
-(19 mm).  All {\it text} must be in a two-column format. Columns are to be 3.39
-inches (86 mm) wide, with a 0.24 inch (6 mm) space between them. Text must be
-fully justified.
-
-\section{PAGE TITLE SECTION}
-\label{sec:pagestyle}
-
-The paper title (on the first page) should begin 1.38 inches (35 mm) from the
-top edge of the page, centered, completely capitalized, and in Times 14-point,
-boldface type.  The authors' name(s) and affiliation(s) appear below the title
-in capital and lower case letters.  Papers with multiple authors and
-affiliations may require two or more lines for this information.
-
-\section{TYPE-STYLE AND FONTS}
-\label{sec:typestyle}
-
-To achieve the best rendering both in the proceedings and from the CD-ROM, we
-strongly encourage you to use Times-Roman font.  In addition, this will give
-the proceedings a more uniform look.  Use a font that is no smaller than nine
-point type throughout the paper, including figure captions.
-
-In nine point type font, capital letters are 2 mm high.  If you use the
-smallest point size, there should be no more than 3.2 lines/cm (8 lines/inch)
-vertically.  This is a minimum spacing; 2.75 lines/cm (7 lines/inch) will make
-the paper much more readable.  Larger type sizes require correspondingly larger
-vertical spacing.  Please do not double-space your paper.  True-Type 1 fonts
-are preferred.
-
-The first paragraph in each section should not be indented, but all the
-following paragraphs within the section should be indented as these paragraphs
-demonstrate.
-
-\section{MAJOR HEADINGS}
-\label{sec:majhead}
-
-Major headings, for example, "1. Introduction", should appear in all capital
-letters, bold face if possible, centered in the column, with one blank line
-before, and one blank line after. Use a period (".") after the heading number,
-not a colon.
-
-\subsection{Subheadings}
-\label{ssec:subhead}
-
-Subheadings should appear in lower case (initial word capitalized) in
-boldface.  They should start at the left margin on a separate line.
-
-\subsubsection{Sub-subheadings}
-\label{sssec:subsubhead}
-
-Sub-subheadings, as in this paragraph, are discouraged. However, if you
-must use them, they should appear in lower case (initial word
-capitalized) and start at the left margin on a separate line, with paragraph
-text beginning on the following line.  They should be in italics.
-
-\section{PRINTING YOUR PAPER}
-\label{sec:print}
-
-Print your properly formatted text on high-quality, 8.5 x 11-inch white printer
-paper. A4 paper is also acceptable, but please leave the extra 0.5 inch (12 mm)
-empty at the BOTTOM of the page and follow the top and left margins as
-specified.  If the last page of your paper is only partially filled, arrange
-the columns so that they are evenly balanced if possible, rather than having
-one long column.
-
-In \LaTeX, to start a new column (but not a new page) and help balance the
-last-page column lengths, you can use the command ``$\backslash$pagebreak'' as
-demonstrated on this page (see the \LaTeX\ source below).
-
-\section{PAGE NUMBERING}
-\label{sec:page}
-
-Please do {\bf not} paginate your paper.  Page numbers, session numbers, and
-conference identification will be inserted when the paper is included in the
-proceedings.
-
-\section{ILLUSTRATIONS, GRAPHS, AND PHOTOGRAPHS}
-\label{sec:illust}
-
-Illustrations must appear within the designated margins.  They may span the two
-columns.  If possible, position illustrations at the top of columns, rather
-than in the middle or at the bottom.  Caption and number every illustration.
-All halftone illustrations must be clear black and white prints.  If you use
-color, make sure that the color figures are clear when printed on a black-only
-printer.
-
-Since there are many ways, often incompatible, of including images (e.g., with
-experimental results) in a \LaTeX\ document, below is an example of how to do
-this \cite{Lamp86}.
+%\section{Formatting your paper}
+%\label{sec:format}
+%
+%All printed material, including text, illustrations, and charts, must be kept
+%within a print area of 7 inches (178 mm) wide by 9 inches (229 mm) high. Do
+%not write or print anything outside the print area. The top margin must be 1
+%inch (25 mm), except for the title page, and the left margin must be 0.75 inch
+%(19 mm).  All {\it text} must be in a two-column format. Columns are to be 3.39
+%inches (86 mm) wide, with a 0.24 inch (6 mm) space between them. Text must be
+%fully justified.
+%
+%\section{PAGE TITLE SECTION}
+%\label{sec:pagestyle}
+%
+%The paper title (on the first page) should begin 1.38 inches (35 mm) from the
+%top edge of the page, centered, completely capitalized, and in Times 14-point,
+%boldface type.  The authors' name(s) and affiliation(s) appear below the title
+%in capital and lower case letters.  Papers with multiple authors and
+%affiliations may require two or more lines for this information.
+%
+%\section{TYPE-STYLE AND FONTS}
+%\label{sec:typestyle}
+%
+%To achieve the best rendering both in the proceedings and from the CD-ROM, we
+%strongly encourage you to use Times-Roman font.  In addition, this will give
+%the proceedings a more uniform look.  Use a font that is no smaller than nine
+%point type throughout the paper, including figure captions.
+%
+%In nine point type font, capital letters are 2 mm high.  If you use the
+%smallest point size, there should be no more than 3.2 lines/cm (8 lines/inch)
+%vertically.  This is a minimum spacing; 2.75 lines/cm (7 lines/inch) will make
+%the paper much more readable.  Larger type sizes require correspondingly larger
+%vertical spacing.  Please do not double-space your paper.  True-Type 1 fonts
+%are preferred.
+%
+%The first paragraph in each section should not be indented, but all the
+%following paragraphs within the section should be indented as these paragraphs
+%demonstrate.
+%
+%\section{MAJOR HEADINGS}
+%\label{sec:majhead}
+%
+%Major headings, for example, "1. Introduction", should appear in all capital
+%letters, bold face if possible, centered in the column, with one blank line
+%before, and one blank line after. Use a period (".") after the heading number,
+%not a colon.
+%
+%\subsection{Subheadings}
+%\label{ssec:subhead}
+%
+%Subheadings should appear in lower case (initial word capitalized) in
+%boldface.  They should start at the left margin on a separate line.
+% 
+%\subsubsection{Sub-subheadings}
+%\label{sssec:subsubhead}
+%
+%Sub-subheadings, as in this paragraph, are discouraged. However, if you
+%must use them, they should appear in lower case (initial word
+%capitalized) and start at the left margin on a separate line, with paragraph
+%text beginning on the following line.  They should be in italics.
+%
+%\section{PRINTING YOUR PAPER}
+%\label{sec:print}
+%
+%Print your properly formatted text on high-quality, 8.5 x 11-inch white printer
+%paper. A4 paper is also acceptable, but please leave the extra 0.5 inch (12 mm)
+%empty at the BOTTOM of the page and follow the top and left margins as
+%specified.  If the last page of your paper is only partially filled, arrange
+%the columns so that they are evenly balanced if possible, rather than having
+%one long column.
+%
+%In \LaTeX, to start a new column (but not a new page) and help balance the
+%last-page column lengths, you can use the command ``$\backslash$pagebreak'' as
+%demonstrated on this page (see the \LaTeX\ source below).
+%
+%\section{PAGE NUMBERING}
+%\label{sec:page}
+%
+%Please do {\bf not} paginate your paper.  Page numbers, session numbers, and
+%conference identification will be inserted when the paper is included in the
+%proceedings.
+%
+%\section{ILLUSTRATIONS, GRAPHS, AND PHOTOGRAPHS}
+%\label{sec:illust}
+%
+%Illustrations must appear within the designated margins.  They may span the two
+%columns.  If possible, position illustrations at the top of columns, rather
+%than in the middle or at the bottom.  Caption and number every illustration.
+%All halftone illustrations must be clear black and white prints.  If you use
+%color, make sure that the color figures are clear when printed on a black-only
+%printer.
+%
+%Since there are many ways, often incompatible, of including images (e.g., with
+%experimental results) in a \LaTeX\ document, below is an example of how to do
+%this \cite{Lamp86}.
 
@@
 
-\section{FOOTNOTES}
-\label{sec:foot}
+%\section{FOOTNOTES}
+%\label{sec:foot}
+%
+%Use footnotes sparingly (or not at all!) and place them at the bottom of the
+%column on the page on which they are referenced. Use Times 9-point type,
+%single-spaced. To help your readers, avoid using footnotes altogether and
+%include necessary peripheral observations in the text (within parentheses, if
+%you prefer, as in this sentence).
+%
 
-Use footnotes sparingly (or not at all!) and place them at the bottom of the
-column on the page on which they are referenced. Use Times 9-point type,
-single-spaced. To help your readers, avoid using footnotes altogether and
-include necessary peripheral observations in the text (within parentheses, if
-you prefer, as in this sentence).
-
-\section{COPYRIGHT FORMS}
-\label{sec:copyright}
-
-You must include your fully completed, signed IEEE copyright release form when
-you submit your paper. We {\bf must} have this form before your paper can be
-published in the proceedings.  The copyright form is available as a Word file,
-a PDF file, and an HTML file. You can also use the form sent with your author
-kit.
+%\section{COPYRIGHT FORMS}
+%\label{sec:copyright}
+%
+%You must include your fully completed, signed IEEE copyright release form when
+%you submit your paper. We {\bf must} have this form before your paper can be
+%published in the proceedings.  The copyright form is available as a Word file,
+%a PDF file, and an HTML file. You can also use the form sent with your author
+%kit.
 
@@
 
-List and number all bibliographical references at the end of the paper.
-The references can be numbered in alphabetic order or in order of appearance in the document.
-When referring to them in the text, type the corresponding reference number in square brackets as shown at the end of this sentence \cite{C2}.
+%List and number all bibliographical references at the end of the
+%paper.  The references can be numbered in alphabetic order or in
+%order of appearance in the document.  When referring to them in the
+%text, type the corresponding reference number in square brackets as
+%shown at the end of this sentence \cite{C2}.
 

### 2016-11-07 Paper.tex
Morphology added

@@
 \name{Peter Naylor$^{1,2,3}$\sthanks{Peter Naylor has received a PhD
-  fellowship from the Ligue contre le Cancer. } \qquad Marick Lae$^{2}$
+  fellowship from the Ligue contre le Cancer. } \qquad Marick La\'e$^{4}$
   \qquad Fabien Reyal$^{2}$\qquad Thomas Walter$^{1,2,3}$}
@@
 $^{2}$Institut Curie, 75248 Paris Cedex, France\\
-$^{3}$INSERM U900, 75248 Paris Cedex, France}
+$^{3}$INSERM U900, 75248 Paris Cedex, France\\
+$^{4}$Service de Pathologie, Institut Curie, 75248 Paris Cedex, France}
 %
@@
 deep learning algorithms have been used recently with great success to
-complex segmentation tasks in biology\cite{Ciresan2012,Ronneberger2015}.
+complex segmentation tasks in biology\cite{Ciresan2012,UNet}.
 
@@
 
+%% Mathematical Morphology
+The results obtained by the Deep Neural Network were encouraging, but
+touching nuclei were often segmented as one single object. This is not
+surprising, as the error at a pixel level seems very minor, and no
+shape prior is used in the model. Solving this issue by weighting the
+error term for pixels between objects did not solve the issue for our
+case (data not shown). However, we did observe that for touching and
+even partially overlapping nuclei, the posterior probability at the
+nucleus border is systematically lower than in
+the putative center of the nucleus, but may still be larger than
+typically applied thresholds.This leads to the following rationale. As in the center of nuclei, the
+posterior probability is maximal, we can readily assume that the local
+maxima of the posterior correspond to putative nuclei, which we call candidates. Let
+$\mathcal{X}=(x_1,x_2,\ldots,x_N)$be a path that joins two candidates
+(i.e. $\forall i x_i$ and $x_{i+1}$ are neighbor pixels) and
+$\mathcal{P}=(p_1,p_2,\ldots,p_N)$ the corresponding posterior
+probabilities. Without loss of generality, we assume $p_1\leq P_N$.
+We define for each path $\mathcal{X}$ a cost
+$C(\mathcal{P})=\max_{i=2 \ldots N}{p_1-p_i}$, which is the maximal
+decrease in posterior probability along the path, when starting from
+the candidate with lower probability.  Considering all paths joining two
+candidates, we can now state a criterion that allows us to decide whether to
+perform a split (and thus accept the candidates as being different
+nuclei) or not: if all the paths involve a decrease in probability
+larger than a parameter $\lambda$, we will perform a
+split. Conversely, if we can find a path that joins the two candidates
+with a probability decrease smaller or equal to $\lambda$, no split
+will be performed: we argue that in this case, it is probably one
+single object. Hence, the split is performed if: 
+\begin{equation}
+\min_{\mathcal{P}}C(\mathcal{P}) = \min_{\mathcal{P}} \{\max_{i=2
+  \ldots N}{p_1-p_i}\} > \lambda
+\end{equation}
+where $\lambda$ is a free parameter. This is actually nothing else
+than the morphological dynamics\cite{Grimaud1992}. The actual split
+locations are thus obtained by applying the watershed algorithm,
+starting from the local maxima of the posterior probability map with
+morphological dynamics larger than a free parameter $\lambda$.
+
+To speed up this procedure, we have developed an algorithm that
+performs selection and Watershed algorithm in a single pass by
+selectively building the Watershed line or fusing the regions,
+depending on the morphological dynamic at the moment at which two
+regions get in contact. This algorithm will be made publicly available
+through the open-source software scikit-image\cite{scikit-image}, in which we implemented
+all the steps which were not related to deep learning.
+
 \section{Different architectures/Results}
-\label{sec:method}
+\label{sec:results}
 We experience with 4 known arhitectures in semantic segmentation, one 
@@
 
-\section{REFERENCES}
-\label{sec:ref}
+%\section{REFERENCES}
+%\label{sec:ref}
 
@@
 \bibliographystyle{IEEEbib}
-\bibliography{strings}
+\bibliography{refs}
 

### 2016-11-07 Paper.tex
new

--- 2016-11-07 Paper.tex
@@
 locate objects within a picture. Different architecture arising from 
-different intuition are also possible and have been applied in this paper
+different intuition are also possible and have been applied in this paper.
+
 Talk about related work.
@@
 was not of the right magnitude the given network did not seem to learn. 
+We therefore fixed the momentum to be 0.9 and the weight decay to be 
+$5.10^{-5}$ for all of the experiences, the learning rate was tunned 
+according to the model choosen.
 We also experienced with different 
@@
 set of pretrained-weights extracted from the classical deep learning 
-architecture. DeconvNet is also based on a classical architecture, 
+architecture, for a more detailed explaination please refer to \cite{long2015fcn}. DeconvNet is also based on a classical architecture, 
 however, in this network their are no skip layer as one intends to learn 
 the proper upsampling threw repeated deconvolution and convolution 
-layers.
-This model can also be fine tuned.
-The final architecture that we tried is the UNet.
-This network combines both contribution of the above networks, the UNet has a similar architecture to the DeconvNet with skip layers.
-\section{Result}
+layers. This model can also be fine tuned, for more information please 
+refer to the original paper \cite{noh2015learning}. We did not
+ensemble classifier as suggested in 
+\cite{noh2015learning} as our FCN and DeconvNet classifier achieve very similar scores.
+% The final architecture that we tried is the UNet. This network combines 
+%both contribution of the above networks, the UNet has a similar 
+%architecture to the DeconvNet with skip layers.
+\section{Result and discussion}
 \label{sec:result}
+We conducted our experiments on GPUs via the caffe framework, \cite{caffe}.
+We present our results in table \ref{tab:resul} where we averaged the metrics other all left out patients.
+We also added, for illustration purposes \ref{fig:prediction}, image prediction and associated probability maps to evaluate some differences between the classifiers.
+We notice that the simpler net, Baochuan Net seems to have learnt simple rules based on color information.
+As we can not notice by the "holes" in the probability map when the interior of the cell is brighter.
+On the contrary, deeper nets as FCN and DeconvNet have learnt deeper features and seem capable of recognizing whole cells.
+The small noticable differences in \ref{fig:prediction} are due to a random crop, this results in a slightly shiffted image for each one of the predictions.
+\begin{table}
+\begin{tabular}{|c|c|c|c|}
+\hline
+  & Baochuan & DeconvNet & FCN \\
+ \hline
+Accuracy  &       0.936 & 0.968 &0.958  \\
+IU   &    0.759 &     0.856 & 0.857 \\
+Recall     &       0.744  &     0.856 & 0.855 \\
+Precision   &       0.741 &     0.858 & 0.878\\
+F1    &       0.742 &     0.856 & 0.866 \\
+TP       &       0.744 &     0.856 & 0.855  \\
+TN      &       0.963 &     0.981 &  0.977\\
+Performance    &       0.853 &     0.918 & 0.916\\
+Pixel error  &  0.063 &     0.032 & 0.042\\
+\hline
+\end{tabular}
+\caption{\label{tab:res}Results}
+\label{tab:res}
+\end{table}
 
-\begin{tabular}{|c|c|c|c|c|c|}
- & UNet & Baochuan & DeconvNet & FCN & Ensemble \\
+%%with Unet
+%\begin{tabular}{|c|c|c|c|c|c|}
+% & UNet & Baochuan & DeconvNet & FCN & Ensemble \\
 %\hrule
-Accuracy          &       0.89 &       0.94 & 0.97\\
-IU   &       0.70 &       0.76 &     0.86 \\
-Recall                     &       0.75 &       0.74  &     0.86 &&\\
-Precision                  &       0.64 &       0.74 &     0.86 &&\\
-F1                         &       0.69 &       0.74 &     0.86 &&  \\
-TP             &       0.75 &       0.74 &     0.86 && \\
-TN             &       0.92 &       0.96 &     0.98 &&\\
-Performance                &       0.84 &       0.85 &     0.92 &&\\
-Pixel error                &       0.11 &       0.06 &     0.03 &&\\
-\end{tabular}
+%Accuracy &       0.89 &       0.936 & 0.968 &0.958 & \\
+%IU   &       0.70 &       0.759 &     0.856 & 0.857 &\\
+%Recall    &       0.75 &       0.744  &     0.856 & 0.855 &\\
+%Precision    &       0.64 &       0.741 &     0.858 & 0.878&\\
+%F1       &       0.69 &       0.742 &     0.856 & 0.866&  \\
+%TP             &       0.75 &       0.744 &     0.856 & 0.855 & \\
+%TN             &       0.92 &       0.963 &     0.981 &  0.977&\\
+%Performance    &       0.84 &       0.853 &     0.918 & 0.916&\\
+%Pixel error  &       0.11 &       0.063 &     0.032 & 0.042&\\
+%\end{tabular}
 
-\section{Discussion}
-\label{sec:discussion}
-What's next?
+\section{PAGE TITLE SECTION}
+\label{sec:pagestyle}
 
-%\section{Formatting your paper}
-%\label{sec:format}
-%
-%All printed material, including text, illustrations, and charts, must be kept
-%within a print area of 7 inches (178 mm) wide by 9 inches (229 mm) high. Do
-%not write or print anything outside the print area. The top margin must be 1
-%inch (25 mm), except for the title page, and the left margin must be 0.75 inch
-%(19 mm).  All {\it text} must be in a two-column format. Columns are to be 3.39
-%inches (86 mm) wide, with a 0.24 inch (6 mm) space between them. Text must be
-%fully justified.
-%
-%\section{PAGE TITLE SECTION}
-%\label{sec:pagestyle}
-%
-%The paper title (on the first page) should begin 1.38 inches (35 mm) from the
-%top edge of the page, centered, completely capitalized, and in Times 14-point,
-%boldface type.  The authors' name(s) and affiliation(s) appear below the title
-%in capital and lower case letters.  Papers with multiple authors and
-%affiliations may require two or more lines for this information.
-%
-%\section{TYPE-STYLE AND FONTS}
-%\label{sec:typestyle}
-%
-%To achieve the best rendering both in the proceedings and from the CD-ROM, we
-%strongly encourage you to use Times-Roman font.  In addition, this will give
-%the proceedings a more uniform look.  Use a font that is no smaller than nine
-%point type throughout the paper, including figure captions.
-%
-%In nine point type font, capital letters are 2 mm high.  If you use the
-%smallest point size, there should be no more than 3.2 lines/cm (8 lines/inch)
-%vertically.  This is a minimum spacing; 2.75 lines/cm (7 lines/inch) will make
-%the paper much more readable.  Larger type sizes require correspondingly larger
-%vertical spacing.  Please do not double-space your paper.  True-Type 1 fonts
-%are preferred.
-%
-%The first paragraph in each section should not be indented, but all the
-%following paragraphs within the section should be indented as these paragraphs
-%demonstrate.
-%
-%\section{MAJOR HEADINGS}
-%\label{sec:majhead}
-%
-%Major headings, for example, "1. Introduction", should appear in all capital
-%letters, bold face if possible, centered in the column, with one blank line
-%before, and one blank line after. Use a period (".") after the heading number,
-%not a colon.
-%
-%\subsection{Subheadings}
-%\label{ssec:subhead}
-%
-%Subheadings should appear in lower case (initial word capitalized) in
-%boldface.  They should start at the left margin on a separate line.
-% 
-%\subsubsection{Sub-subheadings}
-%\label{sssec:subsubhead}
-%
-%Sub-subheadings, as in this paragraph, are discouraged. However, if you
-%must use them, they should appear in lower case (initial word
-%capitalized) and start at the left margin on a separate line, with paragraph
-%text beginning on the following line.  They should be in italics.
-%
-%\section{PRINTING YOUR PAPER}
-%\label{sec:print}
-%
-%Print your properly formatted text on high-quality, 8.5 x 11-inch white printer
-%paper. A4 paper is also acceptable, but please leave the extra 0.5 inch (12 mm)
-%empty at the BOTTOM of the page and follow the top and left margins as
-%specified.  If the last page of your paper is only partially filled, arrange
-%the columns so that they are evenly balanced if possible, rather than having
-%one long column.
-%
-%In \LaTeX, to start a new column (but not a new page) and help balance the
-%last-page column lengths, you can use the command ``$\backslash$pagebreak'' as
-%demonstrated on this page (see the \LaTeX\ source below).
-%
-%\section{PAGE NUMBERING}
-%\label{sec:page}
-%
-%Please do {\bf not} paginate your paper.  Page numbers, session numbers, and
-%conference identification will be inserted when the paper is included in the
-%proceedings.
-%
-%\section{ILLUSTRATIONS, GRAPHS, AND PHOTOGRAPHS}
-%\label{sec:illust}
-%
-%Illustrations must appear within the designated margins.  They may span the two
-%columns.  If possible, position illustrations at the top of columns, rather
-%than in the middle or at the bottom.  Caption and number every illustration.
-%All halftone illustrations must be clear black and white prints.  If you use
-%color, make sure that the color figures are clear when printed on a black-only
-%printer.
-%
-%Since there are many ways, often incompatible, of including images (e.g., with
-%experimental results) in a \LaTeX\ document, below is an example of how to do
-%this \cite{Lamp86}.
+The paper title (on the first page) should begin 1.38 inches (35 mm) from the
+top edge of the page, centered, completely capitalized, and in Times 14-point,
+boldface type.  The authors' name(s) and affiliation(s) appear below the title
+in capital and lower case letters.  Papers with multiple authors and
+affiliations may require two or more lines for this information.
+
+\section{TYPE-STYLE AND FONTS}
+\label{sec:typestyle}
+
+The first paragraph in each section should not be indented, but all the
+following paragraphs within the section should be indented as these paragraphs
+demonstrate.
 
@@
 \begin{figure}[htb]
-
-\begin{minipage}[b]{1.0\linewidth}
-  \centering
-  \centerline{\includegraphics[width=8.5cm]{RGB_1}}
-%  \vspace{2.0cm}
-  \centerline{Patient 498959}\medskip
-\end{minipage}
-%
 \begin{minipage}[b]{.48\linewidth}
@@
 %  \vspace{1.5cm}
-  \centerline{Sample from patient 581910}\medskip
+  \centerline{Another one from patient 581910}\medskip
 \end{minipage}
@@
 
+\begin{figure}[htb]
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{RGB_pred}}
+%  \vspace{1.5cm}
+  \centerline{Original RGB sample}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{GT_pred}}
+%  \vspace{1.5cm}
+  \centerline{Associated ground truth}\medskip
+\end{minipage}
+
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{BaochuanB}}
+%  \vspace{1.5cm}
+  \centerline{BaochuanNet}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{BaochuanP}}
+%  \vspace{1.5cm}
+  \centerline{Probability map}\medskip
+\end{minipage}
+
+%
+%
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{DeconvNetB}}
+%  \vspace{1.5cm}
+  \centerline{DeconvNet}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{DeconvNetP}}
+%  \vspace{1.5cm}
+  \centerline{Probability map}\medskip
+\end{minipage}
+%
+%
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{FCNB}}
+%  \vspace{1.5cm}
+  \centerline{FCN}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{FCNP}}
+%  \vspace{1.5cm}
+  \centerline{Probability map}\medskip
+\end{minipage}
+%
+\caption{Prediction via different classifiers of a random sample on the left out patient: 572123}
+\label{fig:prediction}
+%
+\end{figure}
+
 % To start a new column (but not a new page) and help balance the last-page
@@
 
-%\section{FOOTNOTES}
-%\label{sec:foot}
-%
-%Use footnotes sparingly (or not at all!) and place them at the bottom of the
-%column on the page on which they are referenced. Use Times 9-point type,
-%single-spaced. To help your readers, avoid using footnotes altogether and
-%include necessary peripheral observations in the text (within parentheses, if
-%you prefer, as in this sentence).
-%
+\section{FOOTNOTES}
+\label{sec:foot}
 
-%\section{COPYRIGHT FORMS}
-%\label{sec:copyright}
-%
-%You must include your fully completed, signed IEEE copyright release form when
-%you submit your paper. We {\bf must} have this form before your paper can be
-%published in the proceedings.  The copyright form is available as a Word file,
-%a PDF file, and an HTML file. You can also use the form sent with your author
-%kit.
+Use footnotes sparingly (or not at all!) and place them at the bottom of the
+column on the page on which they are referenced. Use Times 9-point type,
+single-spaced. To help your readers, avoid using footnotes altogether and
+include necessary peripheral observations in the text (within parentheses, if
+you prefer, as in this sentence).
+
+\section{COPYRIGHT FORMS}
+\label{sec:copyright}
+
+You must include your fully completed, signed IEEE copyright release form when
+you submit your paper. We {\bf must} have this form before your paper can be
+published in the proceedings.  The copyright form is available as a Word file,
+a PDF file, and an HTML file. You can also use the form sent with your author
+kit.
 
@@
 
-%List and number all bibliographical references at the end of the
-%paper.  The references can be numbered in alphabetic order or in
-%order of appearance in the document.  When referring to them in the
-%text, type the corresponding reference number in square brackets as
-%shown at the end of this sentence \cite{C2}.
+List and number all bibliographical references at the end of the paper.
+The references can be numbered in alphabetic order or in order of appearance in the document.
+When referring to them in the text, type the corresponding reference number in square brackets as shown at the end of this sentence \cite{C2}.
 

### 2016-11-07 Paper.tex
before merging

@@
 \label{sec:result}
-We conducted our experiments on GPUs via the caffe framework, \cite{caffe}.
-We present our results in table \ref{tab:resul} where we averaged the metrics other all left out patients.
+We conducted our experiments on GPUs via the caffe framework, \cite{jia2014caffe}.
+We present our results in table \ref{tab:res} where we averaged the metrics other all left out patients.
 We also added, for illustration purposes \ref{fig:prediction}, image prediction and associated probability maps to evaluate some differences between the classifiers.

### 2016-11-07 Paper.tex

--- 2016-11-07 Paper.tex
@@
 set of pretrained-weights extracted from the classical deep learning 
-architecture. DeconvNet is also based on a classical architecture, 
+architecture, for a more detailed explaination please refer to \cite{long2015fcn}. DeconvNet is also based on a classical architecture, 
 however, in this network their are no skip layer as one intends to learn 
 the proper upsampling threw repeated deconvolution and convolution 
-layers.
-This model can also be fine tuned.
-The final architecture that we tried is the UNet.
-This network combines both contribution of the above networks, the UNet has a similar architecture to the DeconvNet with skip layers.
-\section{Result}
+layers. This model can also be fine tuned, for more information please 
+refer to the original paper \cite{noh2015learning}. We did not
+ensemble classifier as suggested in 
+\cite{noh2015learning} as our FCN and DeconvNet classifier achieve very similar scores.
+% The final architecture that we tried is the UNet. This network combines 
+%both contribution of the above networks, the UNet has a similar 
+%architecture to the DeconvNet with skip layers.
+\section{Result and discussion}
 \label{sec:result}
+We conducted our experiments on GPUs via the caffe framework, \cite{jia2014caffe}.
+We present our results in table \ref{tab:res} where we averaged the metrics other all left out patients.
+We also added, for illustration purposes \ref{fig:prediction}, image prediction and associated probability maps to evaluate some differences between the classifiers.
+We notice that the simpler net, Baochuan Net seems to have learnt simple rules based on color information.
+As we can not notice by the "holes" in the probability map when the interior of the cell is brighter.
+On the contrary, deeper nets as FCN and DeconvNet have learnt deeper features and seem capable of recognizing whole cells.
+The small noticable differences in \ref{fig:prediction} are due to a random crop, this results in a slightly shiffted image for each one of the predictions.
+\begin{table}
+\begin{tabular}{|c|c|c|c|}
+\hline
+  & Baochuan & DeconvNet & FCN \\
+ \hline
+Accuracy  &       0.936 & 0.968 &0.958  \\
+IU   &    0.759 &     0.856 & 0.857 \\
+Recall     &       0.744  &     0.856 & 0.855 \\
+Precision   &       0.741 &     0.858 & 0.878\\
+F1    &       0.742 &     0.856 & 0.866 \\
+TP       &       0.744 &     0.856 & 0.855  \\
+TN      &       0.963 &     0.981 &  0.977\\
+Performance    &       0.853 &     0.918 & 0.916\\
+Pixel error  &  0.063 &     0.032 & 0.042\\
+\hline
+\end{tabular}
+\caption{\label{tab:res}Results}
+\label{tab:res}
+\end{table}
 
-\begin{tabular}{|c|c|c|c|c|c|}
- & UNet & Baochuan & DeconvNet & FCN & Ensemble \\
+%%with Unet
+%\begin{tabular}{|c|c|c|c|c|c|}
+% & UNet & Baochuan & DeconvNet & FCN & Ensemble \\
 %\hrule
-Accuracy          &       0.89 &       0.94 & 0.97\\
-IU   &       0.70 &       0.76 &     0.86 \\
-Recall                     &       0.75 &       0.74  &     0.86 &&\\
-Precision                  &       0.64 &       0.74 &     0.86 &&\\
-F1                         &       0.69 &       0.74 &     0.86 &&  \\
-TP             &       0.75 &       0.74 &     0.86 && \\
-TN             &       0.92 &       0.96 &     0.98 &&\\
-Performance                &       0.84 &       0.85 &     0.92 &&\\
-Pixel error                &       0.11 &       0.06 &     0.03 &&\\
-\end{tabular}
-
-\section{Discussion}
-\label{sec:discussion}
-What's next?
+%Accuracy &       0.89 &       0.936 & 0.968 &0.958 & \\
+%IU   &       0.70 &       0.759 &     0.856 & 0.857 &\\
+%Recall    &       0.75 &       0.744  &     0.856 & 0.855 &\\
+%Precision    &       0.64 &       0.741 &     0.858 & 0.878&\\
+%F1       &       0.69 &       0.742 &     0.856 & 0.866&  \\
+%TP             &       0.75 &       0.744 &     0.856 & 0.855 & \\
+%TN             &       0.92 &       0.963 &     0.981 &  0.977&\\
+%Performance    &       0.84 &       0.853 &     0.918 & 0.916&\\
+%Pixel error  &       0.11 &       0.063 &     0.032 & 0.042&\\
+%\end{tabular}
 
@@
 \label{fig:annotation}
+%
+\end{figure}
+
+\begin{figure}[htb]
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{RGB_pred}}
+%  \vspace{1.5cm}
+  \centerline{Original RGB sample}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{GT_pred}}
+%  \vspace{1.5cm}
+  \centerline{Associated ground truth}\medskip
+\end{minipage}
+
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{BaochuanB}}
+%  \vspace{1.5cm}
+  \centerline{BaochuanNet}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{BaochuanP}}
+%  \vspace{1.5cm}
+  \centerline{Probability map}\medskip
+\end{minipage}
+
+%
+%
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{DeconvNetB}}
+%  \vspace{1.5cm}
+  \centerline{DeconvNet}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{DeconvNetP}}
+%  \vspace{1.5cm}
+  \centerline{Probability map}\medskip
+\end{minipage}
+%
+%
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{FCNB}}
+%  \vspace{1.5cm}
+  \centerline{FCN}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{FCNP}}
+%  \vspace{1.5cm}
+  \centerline{Probability map}\medskip
+\end{minipage}
+%
+\caption{Prediction via different classifiers of a random sample on the left out patient: 572123}
+\label{fig:prediction}
 %

### 2016-11-07 Paper.tex
correction 1

@@
 stainned histopathology images with their associated ground truth. Each 
-ground truth image is a $512 \times 512$ where each pixel value above 
+ground truth image is a $512 \times 512$ image where each pixel value above 
 $0$ is considered as a pixel belonging to a nuclei. The differences in 
@@
 three annotated images. This annotation was conducted via the help of 
-the software ITK-snap and were annotated by the authors of the paper.
+the software ITK-snap, \cite{py06nimg} http://www.itksnap.org, and were annotated by the authors of the paper.
 
@@
 breast cells, fibroblasts,  endothelial cells, fat cells, macrophage cells and 
-inflammatory cells (lymphocytes and plasmocytes). For the moment, cell types have not been seperated, which means that in this dataset every annotation corresponds to a global type of cell.
+inflammatory cells (lymphocytes and plasmocytes). For the moment, cell types have not been seperated, which means that in this dataset every annotation corresponds to a global type: cell.
 
@@
  $\frac{1}{\sum_{i,j}w_{ij}} \sum_{i,j} \sum_k w_{i,j} t_{i,j,k} \log (\widehat{p_{i,j,k}})$
-, where $k$ designates a certain label, $w_{i,j}$ is 
+, where $k$ designates a certain label, $w_{i,j}$ is a 
 certain weight given to pixel $i,j$, $t_{i,j,k}$ is equal to 1 if pixel $i,j$ is 
@@
 We have our training set $(A_l,B_l)_{l \in [1, N]}$ where N is equal to 
-34, how ever each element $A_l$ belongs to a certain patients and 
+33, how ever each element $A_l$ belongs to a certain patients and 
 several elements $A_l$ can belong to the same patient. As we are 
@@
 Our final score is averaged over all patients.
-Several metrics assess the quality of the model, the accuracy (Acc), the 
-F1 score and a performance (Perf) score which is the mean between the 
-true positive rates and the true negative rates.
+Several metrics assess the quality of the model, the accuracy, the 
+F1 score and a performance score which is the mean between the 
+true positive rate and the true negative rate.
 
@@
 maxima of the posterior correspond to putative nuclei, which we call candidates. Let
-$\mathcal{X}=(x_1,x_2,\ldots,x_N)$be a path that joins two candidates
-(i.e. $\forall i x_i$ and $x_{i+1}$ are neighbor pixels) and
+$\mathcal{X}=(x_1,x_2,\ldots,x_N)$ be a path that joins two candidates
+(i.e. $\forall i, \ x_i$ and $x_{i+1}$ are neighbor pixels) and
 $\mathcal{P}=(p_1,p_2,\ldots,p_N)$ the corresponding posterior
@@
 \label{sec:results}
-We experience with 4 known arhitectures in semantic segmentation, one 
-will be named BaochuanNet, Fully Convolutionnal Net (FCN), DeconvNet, 
-UNet. The most basic architecture, BaochuanNet, consists of 4 
-convolutionnal layer where each convolutionnal layer has 8 feature map. 
+We experience with 3 known arhitectures in semantic segmentation, named PangNet, Fully Convolutionnal Net (FCN) and DeconvNet. The most basic architecture, PangNet, consists of 4 
+convolutionnal layer where each convolutionnal layer has 8 feature map, for more information please refer to \cite{pang2010cell}. 
 This net, being not deep, has the advantage of being less 
@@
 ensemble classifier as suggested in 
-\cite{noh2015learning} as our FCN and DeconvNet classifier achieve very similar scores.
+\cite{noh2015learning} as our FCN and DeconvNet classifier achieve very similar scores on the test sets.
 % The final architecture that we tried is the UNet. This network combines 
@@
 We also added, for illustration purposes \ref{fig:prediction}, image prediction and associated probability maps to evaluate some differences between the classifiers.
-We notice that the simpler net, Baochuan Net seems to have learnt simple rules based on color information.
+We notice that the simpler net, PangNet seems to have learnt simple rules such as color information.
 As we can not notice by the "holes" in the probability map when the interior of the cell is brighter.
 On the contrary, deeper nets as FCN and DeconvNet have learnt deeper features and seem capable of recognizing whole cells.
-The small noticable differences in \ref{fig:prediction} are due to a random crop, this results in a slightly shiffted image for each one of the predictions.
+.
 \begin{table}
@@
 \hline
-  & Baochuan & DeconvNet & FCN \\
+  & PangNet & DeconvNet & FCN \\
  \hline
@@
 \end{tabular}
-\caption{\label{tab:res}Results}
+\caption{Results}
 \label{tab:res}
@@
 %\begin{tabular}{|c|c|c|c|c|c|}
-% & UNet & Baochuan & DeconvNet & FCN & Ensemble \\
+% & UNet & PangNet & DeconvNet & FCN & Ensemble \\
 %\hrule
@@
 %  \vspace{1.5cm}
-  \centerline{BaochuanNet}\medskip
+  \centerline{PangNet}\medskip
 \end{minipage}

### 2016-11-07 Paper.tex
correction 2

@@
 \label{sec:related}
+
+In \cite{Drelie08-298}, they have a partially annotated data set of histopathology images for nuclei segmentation.
+
 Image segmentation and object recognition in medical imagining have 
@@
 possible and yield comparable results in terms of accuracy, in 
-\cite{ranefall2016fast} they segment the picture using a ellispe fit 
-which is considerably faster than other state of the art methods. Graph-
-based tools for segmentation are also possible in histopathology 
-\cite{ta2009graph}. \cite{manivannanlocal} focus on gland 
-segmentation, they achieve good results by predicting image patches as 
-a whole, via a classification scheme. The output confidence vector is 
-then preprocessed to obtain the final segmentation. Alternative methods 
+\cite{ranefall2016fast} they segment the picture using mathematical 
+morphology with an ellispe fit condition 
+which is considerably faster than other state of the art methods. 
+%Graph-
+%based tools for segmentation are also possible in histopathology 
+%\cite{ta2009graph}. 
+%\cite{manivannanlocal} focus on gland 
+%segmentation, they achieve good results by predicting image patches as 
+%a whole, via a classification scheme. The output confidence vector is 
+%then preprocessed to obtain the final segmentation. 
+Alternative methods 
 have arisen from the achieving Convolutional neural networks 
@@
 
-Talk about related work.
-
 \section{DataSet}
@@
 nuclei detection dataset within HE stainned histopathology images which 
-can be found at website %\url{www.cbio.ensmp.fr:/pnaylor/download/dataset.zip} 
+can be found at website \url{http://cbio.mines-paristech.fr/~pnaylor/Downloads/HECellSegmentation.zip} 
 (not a true address). This annotated dataset provides images clustered by 
@@
 three annotated images. This annotation was conducted via the help of 
-the software ITK-snap, \cite{py06nimg} http://www.itksnap.org, and were annotated by the authors of the paper.
+the software ITK-snap, \cite{py06nimg} \url{http://www.itksnap.org}, and were annotated by the authors of the paper.
 
@@
 %%Data set description 
+%% I asked Marick's help for this paragraph!
 In this data set we have annotated a considerous amount of cells,
-including normal breast cells (epithelial and lobule cells),  cancerous 
-breast cells, fibroblasts,  endothelial cells, fat cells, macrophage cells and 
-inflammatory cells (lymphocytes and plasmocytes). For the moment, cell types have not been seperated, which means that in this dataset every annotation corresponds to a global type: cell.
+including normal epithelial and myoepithelial breast cells (localized in
+ducts and lobules), invasive carcinomatous cells, fibroblasts, endothelial
+cells, adipocytes, macrophages and
+inflammatory cells (lymphocytes and plasmocytes). For the moment, cell 
+types have not been included, which means that in this dataset every annotation corresponds to a global type: cell.
+We can also give some simple statistics with respect to the dataset.
+We have 33 images with a total of 2754 annotated cells, the maximum number of cells in one sample is 293 and the minimum number of cells in one sample is 5.
+We also have on average 83 cells per sample with a high standard deviation of 63.
 
-\begin{itemize}
-\item Number of images: 33 \\
-\item Number  of cells: 2754 \\
-\item Maximum number of cells in one sample: 293 \\
-\item Minimum number of cells in one sample: 5 \\
-\item Mean number of cells: 83 \\
-\item Standard deviation of number of cells: 63 \\
-\end{itemize}
+% \begin{itemize}
+% \item Number of images: 33 \\
+% \item Number  of cells: 2754 \\
+% \item Maximum number of cells in one sample: 293 \\
+% \item Minimum number of cells in one sample: 5 \\
+% \item Mean number of cells: 83 \\
+% \item Standard deviation of number of cells: 63 \\
+% \end{itemize}
 
@@
 \label{sec:result}
-We conducted our experiments on GPUs via the caffe framework, \cite{jia2014caffe}.
-We present our results in table \ref{tab:res} where we averaged the metrics other all left out patients.
-We also added, for illustration purposes \ref{fig:prediction}, image prediction and associated probability maps to evaluate some differences between the classifiers.
-We notice that the simpler net, PangNet seems to have learnt simple rules such as color information.
-As we can not notice by the "holes" in the probability map when the interior of the cell is brighter.
-On the contrary, deeper nets as FCN and DeconvNet have learnt deeper features and seem capable of recognizing whole cells.
-.
+We conducted our experiments on GPUs via the caffe framework, 
+\cite{jia2014caffe}. We present our results in table \ref{tab:res} where 
+we averaged the metrics other all left out patients. We also added, for 
+illustration purposes \ref{fig:prediction}, image predictions and 
+associated 
+probability maps to evaluate some differences between the classifiers. 
+We notice that the simpler net, PangNet seems to have learnt simple 
+rules such as color information. As we can not notice by the "holes" in 
+the probability map when the interior of the cell is very bright. On the 
+contrary, deeper nets as FCN and DeconvNet have learnt deeper features 
+and seem capable of recognizing whole cells. On these probability maps 
+we applied our watershed segmentation and we can picture the results in 
+the third 
+column. Our post-processing 
+scheme is very sensitive to noise as we can see in the PangNet 
+prediction, many unrelated minimas will lead to highly partitionned cell. 
+This phenomenom also appears with the DeconvNet where undesired 
+cuts were performed, like for the cell at the bottom left of the image. 
+We picked $\lambda = 7$ which seemed to give a nice partitionning of 
+the image, this value can be found by cross validation or by simple 
+visualation of the results.
 \begin{table}
@@
 \end{table}
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+%I don't really know if we need something like this...
 
@@
 
-\begin{minipage}[b]{0.48\linewidth}
+\begin{minipage}[b]{0.32\linewidth}
   \centering
-  \centerline{\includegraphics[height=4.0cm]{BaochuanB}}
+  \centerline{\includegraphics[height=2.4cm]{BaochuanB}}
 %  \vspace{1.5cm}
@@
 \hfill
-\begin{minipage}[b]{.48\linewidth}
+\begin{minipage}[b]{.32\linewidth}
   \centering
-  \centerline{\includegraphics[height=4.0cm]{BaochuanP}}
+  \centerline{\includegraphics[height=2.5cm]{BaochuanP}}
 %  \vspace{1.5cm}
   \centerline{Probability map}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{Baochuan_WS}}
+%  \vspace{1.5cm}
+  \centerline{Watershed}\medskip
 \end{minipage}
@@
 %
-\begin{minipage}[b]{.48\linewidth}
+\begin{minipage}[b]{0.32\linewidth}
   \centering
-  \centerline{\includegraphics[height=4.0cm]{DeconvNetB}}
+  \centerline{\includegraphics[height=2.4cm]{DeconvNetB}}
 %  \vspace{1.5cm}
@@
 \hfill
-\begin{minipage}[b]{0.48\linewidth}
+\begin{minipage}[b]{.32\linewidth}
   \centering
-  \centerline{\includegraphics[height=4.0cm]{DeconvNetP}}
+  \centerline{\includegraphics[height=2.4cm]{DeconvNetP}}
 %  \vspace{1.5cm}
@@
 \end{minipage}
+\hfill
+\begin{minipage}[b]{.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{DeconvNet_WS}}
+%  \vspace{1.5cm}
+  \centerline{Watershed}\medskip
+\end{minipage}
 %
-%
-\begin{minipage}[b]{.48\linewidth}
+\begin{minipage}[b]{0.32\linewidth}
   \centering
-  \centerline{\includegraphics[height=4.0cm]{FCNB}}
+  \centerline{\includegraphics[height=2.4cm]{FCNB}}
 %  \vspace{1.5cm}
@@
 \hfill
-\begin{minipage}[b]{0.48\linewidth}
+\begin{minipage}[b]{.32\linewidth}
   \centering
-  \centerline{\includegraphics[height=4.0cm]{FCNP}}
+  \centerline{\includegraphics[height=2.4cm]{FCNP}}
 %  \vspace{1.5cm}
@@
 \end{minipage}
+\hfill
+\begin{minipage}[b]{.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{FCN_WS}}
+%  \vspace{1.5cm}
+  \centerline{Watershed}\medskip
+\end{minipage}
 %
-\caption{Prediction via different classifiers of a random sample on the left out patient: 572123}
+\caption{Prediction via different classifiers of a random sample on the left out patient: 581910}
 \label{fig:prediction}

### 2016-11-07 Paper.tex
correction 2
abstract

@@
 \address{$^{1}$MINES ParisTech, PSL Research University, CBIO - Centre
-  de Bioinformatique,\\ 
-  35 rue St Honoré 77300 Fontainebleau, France \\
-$^{2}$Institut Curie, 75248 Paris Cedex, France\\
-$^{3}$INSERM U900, 75248 Paris Cedex, France\\
-$^{4}$Service de Pathologie, Institut Curie, 75248 Paris Cedex, France}
+  de Bioinformatique, 35 rue St Honoré 77300 Fontainebleau, France; 
+$\quad ^{2}$Institut Curie, 75248 Paris Cedex, France; 
+$\quad ^{3}$INSERM U900, 75248 Paris Cedex, France; 
+$\quad ^{4}$Service de Pathologie, Institut Curie, 75248 Paris Cedex,
+France;
+$\quad ^{5}$Residual Tumor \& Response to Treatment Laboratory,
+RT2Lab, Translational Research Department, Institut Curie, 26, rue d’Ulm, Paris, F-75248, France;
+$\quad ^{6}$U932, Immunity and Cancer, INSERM, Institut Curie, Paris, F-75248, France;
+$\quad ^{7}$Department of Surgery, Institut Curie, Paris, F-75248, France.
+}
 %
@@
 \begin{abstract}
-%The abstract should appear at the top of the left-hand column of text, about
-%0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
-%length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
-%beginning of the main text.  The abstract should contain about 100 to 150
-%words, and should be identical to the abstract text submitted electronically
-%along with the paper cover sheet.  All manuscripts must be in English, printed
-%in black ink.
+Analysis and interpretation of stained tumor sections is one of the
+main tools in cancer diagnosis and prognosis, which is mainly carried
+out manually by pathologists. The avent of digital pathology provides
+us with the challenging opportunity to automatically analyze large
+amounts of these complex and large image data in order to draw
+biological conclusions from them and to study cellular and tissular
+phenotypes at a large scale. One of the bottlenecks for such an
+approach is the automatic segmentation of cell nuclei from this type
+of image data. Here, we present a fully automated workflow to segment
+nuclei from histopathology image data by training a deep neural
+network on a set of annotated images and by proposing a postprocessing
+step of the posterior probability maps to split jointly segmented
+nuclei. Further, we provide the image data set that has been generated
+for this study as a benchmark set to the scientific community.  
 \end{abstract}
@@
 \begin{keywords}
-Deep Learnnig, Convolutional Neural Networks, Nuclei Segmentation,
-Histpathology, Digital Pathology, Breast Cancer, Cellular Phenotyping
+Deep Learning, Convolutional Neural Networks, Nuclei Segmentation,
+Histopathology, Digital Pathology, Breast Cancer, Cellular Phenotyping
 \end{keywords}
@@
 
-In \cite{Drelie08-298}, they have a partially annotated data set of histopathology images for nuclei segmentation.
+In \cite{Drelie08-298}, they have a partially annotated data set of 
+histopathology images for nuclei segmentation.
+
+%% fill in more information about that dataset
 

### 2016-11-07 Paper.tex
noindent

--- 2016-11-07 Paper.tex
@@
 % images in cancer research, histopathology --> digital pathology
-Today, large sequencing approaches build the main body of cancer
+\noindent Today, large sequencing approaches build the main body of cancer
 research programs and they have revolutionized our understanding of

### 2016-11-07 Paper.tex
tiny paragraph

@@
 
-In \cite{Drelie08-298}, they have a partially annotated data set of 
-histopathology images for nuclei segmentation.
+\noindent In \cite{Drelie08-298}, they have a partially annotated data set for segmentation of 
+histopathology images for nuclei segmentation.   However their study does not sollely focus on tripple negativ breast cancer patients and not only segmentation.
 
@@
 %% Contribution as a dataset, small introduction
-One of the main contributions of this paper is the now public available 
+\noindent One of the main contributions of this paper is the now public available 
 nuclei detection dataset within HE stainned histopathology images which 
@@
 %% Segmentation task
-Let A be the space of RGB images, A can typically be 
+\noindent Let A be the space of RGB images, A can typically be 
 $\mathbb{R}^{n \times p \times 3}$ and let B the space B the space of annotation 
@@
 \label{sec:result}
-We conducted our experiments on GPUs via the caffe framework, 
+\noindent We conducted our experiments on GPUs via the caffe framework, 
 \cite{jia2014caffe}. We present our results in table \ref{tab:res} where 

### 2016-11-07 Paper.tex
dinner

@@
 layers. This model can also be fine tuned, for more information please 
-refer to the original paper \cite{noh2015learning}. We did not
-ensemble classifier as suggested in 
-\cite{noh2015learning} as our FCN and DeconvNet classifier achieve very similar scores on the test sets.
+refer to the original paper \cite{noh2015learning}. We also did an
+ensemble classifier of these two previous nets as suggested in 
+\cite{noh2015learning}.
 % The final architecture that we tried is the UNet. This network combines 
@@
 \begin{table}
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-  & PangNet & DeconvNet & FCN \\
+  & PangNet & DeconvNet & FCN & Ensemble\\
  \hline
-Accuracy  &       0.936 & 0.968 &0.958  \\
-IU   &    0.759 &     0.856 & 0.857 \\
-Recall     &       0.744  &     0.856 & 0.855 \\
-Precision   &       0.741 &     0.858 & 0.878\\
-F1    &       0.742 &     0.856 & 0.866 \\
-TP       &       0.744 &     0.856 & 0.855  \\
-TN      &       0.963 &     0.981 &  0.977\\
-Performance    &       0.853 &     0.918 & 0.916\\
-Pixel error  &  0.063 &     0.032 & 0.042\\
+Accuracy  &       0.936 & 0.968 &0.958 & 0.968  \\
+IU   &    0.759 &     0.856 & 0.857 & 0.861 \\
+Recall     &       0.744  &     0.856 & 0.855 & 0.876\\
+Precision   &       0.741 &     0.858 & 0.878 & 0.851\\
+F1    &       0.742 &     0.856 & 0.866  & 0.863\\
+TP       &       0.744 &     0.856 & 0.855 & 0.876 \\
+TN      &       0.963 &     0.981 &  0.977 & 0.979\\
+Performance    &       0.853 &     0.918 & 0.916 & 0.928\\
+Pixel error  &  0.063 &     0.032 & 0.042 & 0.032\\
 \hline

### 2016-11-07 Paper.tex
Intro shortened

--- 2016-11-07 Paper.tex
@@
 \usepackage{hyperref}
+\usepackage{seqsplit}
 
@@
 \name{Peter Naylor$^{1,2,3}$\sthanks{Peter Naylor has received a PhD
-  fellowship from the Ligue contre le Cancer. } \qquad Marick La\'e$^{4}$
-  \qquad Fabien Reyal$^{2}$\qquad Thomas Walter$^{1,2,3}$}
+  fellowship from the Ligue contre le Cancer} \qquad Marick La\'e$^{4}$
+  \qquad Fabien Reyal$^{5,6,7}$\qquad Thomas Walter$^{1,2,3}$}
 
-\address{$^{1}$MINES ParisTech, PSL Research University, CBIO - Centre
-  de Bioinformatique,\\ 
-  35 rue St Honoré 77300 Fontainebleau, France \\
-$^{2}$Institut Curie, 75248 Paris Cedex, France\\
-$^{3}$INSERM U900, 75248 Paris Cedex, France\\
-$^{4}$Service de Pathologie, Institut Curie, 75248 Paris Cedex, France}
+\address{\normalsize $^{1}$MINES ParisTech, PSL Research University, CBIO - Centre
+  de Bioinformatique, 77300 Fontainebleau, France;\\
+\normalsize $\quad ^{2}$Institut Curie,  
+$\quad ^{3}$INSERM U900, Paris, 
+$\quad ^{4}$Service de Pathologie, Institut Curie, Paris, F-75248, France\\
+\normalsize $\quad ^{5}$Residual Tumor \& Response to Treatment Laboratory,
+RT2Lab, Translational Research Department, Institut Curie, \\
+\normalsize $\quad ^{6}$U932, Immunity and Cancer, INSERM, Institut Curie, 
+$\quad ^{7}$Department of Surgery, Institut Curie, Paris, F-75248, France.
+}
 %
@@
 \begin{abstract}
-%The abstract should appear at the top of the left-hand column of text, about
-%0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
-%length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
-%beginning of the main text.  The abstract should contain about 100 to 150
-%words, and should be identical to the abstract text submitted electronically
-%along with the paper cover sheet.  All manuscripts must be in English, printed
-%in black ink.
+Analysis and interpretation of stained tumor sections is one of the
+main tools in cancer diagnosis and prognosis, which is mainly carried
+out manually by pathologists. The avent of digital pathology provides
+us with the challenging opportunity to automatically analyze large
+amounts of these complex image data in order to draw
+biological conclusions from them and to study cellular and tissular
+phenotypes at a large scale. One of the bottlenecks for such
+approaches is the automatic segmentation of cell nuclei from this type
+of image data. Here, we present a fully automated workflow to segment
+nuclei from histopathology image data by using deep neural
+networks trained from a set of manually annotated images and by processing
+the posterior probability maps in order to split jointly segmented
+nuclei. Further, we provide the image data set that has been generated
+for this study as a benchmark set to the scientific community.  
 \end{abstract}
@@
 % images in cancer research, histopathology --> digital pathology
-\noindent Today, large sequencing approaches build the main body of cancer
+Today, large sequencing approaches build the main body of cancer
 research programs and they have revolutionized our understanding of
@@
 build tools for the quantitative and automatic analysis of these
-complex and informative image data. Indeed, this is a very promising
-approach for several reasons: image based approaches
-provide us with spatial information that is absent in genomic,
-transcriptomic and epigenetic studies of cancer. In addition they
-allow analysis of individual cells, such that it is possible to study
-cellular heterogeneity. Cellular heterogeneity has been acknowledged
-to be of major importance in cancer research and treatment. Also, it
-is possible to analyze cells in terms of morphology and phenotype,
-which brings in a complementary piece of functionally relevant
-information.
+complex and informative image data. These image data are in many ways
+complementary to genomic and expression data, as they are informative
+about the spatial dimension, they allow one to assess cellular
+heterogeneity and allow for single cell analysis in terms of
+morphology and phenotype.
 

### 2016-11-07 Paper.tex
ensemble

--- 2016-11-07 Paper.tex
@@
 \address{$^{1}$MINES ParisTech, PSL Research University, CBIO - Centre
-  de Bioinformatique, 35 rue St Honoré 77300 Fontainebleau, France; 
-$\quad ^{2}$Institut Curie, 75248 Paris Cedex, France; 
-$\quad ^{3}$INSERM U900, 75248 Paris Cedex, France; 
-$\quad ^{4}$Service de Pathologie, Institut Curie, 75248 Paris Cedex,
-France;
-$\quad ^{5}$Residual Tumor \& Response to Treatment Laboratory,
-RT2Lab, Translational Research Department, Institut Curie, 26, rue d’Ulm, Paris, F-75248, France;
-$\quad ^{6}$U932, Immunity and Cancer, INSERM, Institut Curie, Paris, F-75248, France;
-$\quad ^{7}$Department of Surgery, Institut Curie, Paris, F-75248, France.
-}
+  de Bioinformatique,\\ 
+  35 rue St Honoré 77300 Fontainebleau, France \\
+$^{2}$Institut Curie, 75248 Paris Cedex, France\\
+$^{3}$INSERM U900, 75248 Paris Cedex, France\\
+$^{4}$Service de Pathologie, Institut Curie, 75248 Paris Cedex, France}
 %
@@
 \begin{abstract}
-Analysis and interpretation of stained tumor sections is one of the
-main tools in cancer diagnosis and prognosis, which is mainly carried
-out manually by pathologists. The avent of digital pathology provides
-us with the challenging opportunity to automatically analyze large
-amounts of these complex and large image data in order to draw
-biological conclusions from them and to study cellular and tissular
-phenotypes at a large scale. One of the bottlenecks for such an
-approach is the automatic segmentation of cell nuclei from this type
-of image data. Here, we present a fully automated workflow to segment
-nuclei from histopathology image data by training a deep neural
-network on a set of annotated images and by proposing a postprocessing
-step of the posterior probability maps to split jointly segmented
-nuclei. Further, we provide the image data set that has been generated
-for this study as a benchmark set to the scientific community.  
+%The abstract should appear at the top of the left-hand column of text, about
+%0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
+%length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
+%beginning of the main text.  The abstract should contain about 100 to 150
+%words, and should be identical to the abstract text submitted electronically
+%along with the paper cover sheet.  All manuscripts must be in English, printed
+%in black ink.
 \end{abstract}
@@
 \begin{keywords}
-Deep Learning, Convolutional Neural Networks, Nuclei Segmentation,
-Histopathology, Digital Pathology, Breast Cancer, Cellular Phenotyping
+Deep Learnnig, Convolutional Neural Networks, Nuclei Segmentation,
+Histpathology, Digital Pathology, Breast Cancer, Cellular Phenotyping
 \end{keywords}
@@
 %
+\begin{minipage}[b]{0.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{EnsembleB}}
+%  \vspace{1.5cm}
+  \centerline{Ensemble}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{EnsembleP}}
+%  \vspace{1.5cm}
+  \centerline{Probability map}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{Ensemble_WS}}
+%  \vspace{1.5cm}
+  \centerline{Watershed}\medskip
+\end{minipage}
 \caption{Prediction via different classifiers of a random sample on the left out patient: 581910}

### 2016-11-07 Paper.tex
no indent
shortened

--- 2016-11-07 Paper.tex
@@
 %
+
 \begin{document}
@@
 \maketitle
+\vspace{-1cm}
 %
@@
 build tools for the quantitative and automatic analysis of these
-complex and informative image data. These image data are in many ways
-complementary to genomic and expression data, as they are informative
-about the spatial dimension, they allow one to assess cellular
-heterogeneity and allow for single cell analysis in terms of
-morphology and phenotype.
+complex and informative image data, which are complementary to genomic
+and expression data.
 
-% two approaches: CAD vs. understanding
+%These image data are in many ways
+%complementary to genomic and expression data, as they are informative
+%about the spatial dimension, they allow one to assess cellular
+%heterogeneity and they enable single cell analysis in terms of
+%morphology and phenotype.
+
+% two approaches: CAD vs. understanding, importance of segmentation
 For these reasons, analysis of histopathology data has received much
-attention over the last years. Most of these works are in the frame of
-Computer Aided Diagnosis (CAD) and aim at automatically performing the
-task of a human pathologist or at assisting in the diagnosis. For such
-a task, the nature of the features according to which a certain
-classification or detection task is solved is mostly
-irrelevant. A conceptually different approach is to derive biologically
-relevant features, such as phenotype distributions, spatial cell type
-distributions or heterogeneity measures from the tissue data in order to reach some
-understanding as of which biological features can be predictive for
-clinical variables such as resistance to treatment or relapse
-probability.
+attention over the last years. While many approaches aim at
+automatically performing the task of a human pathologist (Computer
+Aided Diagnosis, CAD), we want to investigate the influence of
+biologically relevant features, such as phenotype distributions or
+heterogeneity measures from the tissue data on different clinical
+variables, such as resistance to treatment or relapse probability.
+One essential step is thus the segmentation of nuclei from tissue
+images,  in order to assign them a cell type or phenotypic label and
+to evaluate their spatial distribution.
+
+%Most of these works are in the frame of
+%Computer Aided Diagnosis (CAD) and aim at automatically performing the
+%task of a human pathologist or at assisting in the diagnosis. For such
+%a task, the nature of the features according to which a certain
+%classification or detection task is solved is mostly
+%irrelevant. A conceptually different approach is to derive biologically
+%relevant features, such as phenotype distributions, spatial cell type
+%distributions or heterogeneity measures from the tissue data in order to reach some
+%understanding as of which biological features can be predictive for
+%clinical variables such as resistance to treatment or relapse
+%probability.
 
@@
 % tissues. 
-In this latter case, one of the essential steps is to
-segment nuclei from tissue images in order to be able to
-assign them a cell type or phenotypic label and to evaluate their
-spatial distribution. We concentrate on nuclei, as they are indicative
-of many cellular phenotypes\cite{Chow2012}, and their morphology is 
-currently used by pathologists in order to
-identify the mitotic index and the level of nuclear
-pleomorphism\cite{Elston1991}.
+%In this latter case, one of the essential steps is to
+%segment nuclei from tissue images in order to be able to
+%assign them a cell type or phenotypic label and to evaluate their
+%spatial distribution. We concentrate on nuclei, as they are indicative
+%of many cellular phenotypes\cite{Chow2012}, and their morphology is 
+%currently used by pathologists in order to
+%identify the mitotic index and the level of nuclear
+%pleomorphism\cite{Elston1991}.
 
-Yet, segmentation of nuclei is a
+However, segmentation of nuclei is a
 complicated task: tissue type, staining differences and cell type
@@
 
-The contribution of this paper is three-fold: (1) we have generated a
-ground truth of annotated images containing segmentation results for
-more than 2000 cells. The dataset can be used by the scientific
-community. (2) We apply a deep neural network end-to-end strategy and
+The contribution of this paper is three-fold: (1) we generated a
+set of manually annotated, representative images containing segmentation results for
+more than 2000 cells. We believe that such datasets
+can trigger methodological developments and are
+important for the field. (2) We apply a deep neural network end-to-end strategy and
 demonstrate the superiority of this approach with respect to
@@
 post-processing strategy of the posterior probabilities provided by
-the network. This post-processing strategy is based on mathematical
-morphology and has a rigorous interpretation as to when objects are to
-be split.
+the network. This approach is based on mathematical
+morphology and unlike many adhoc procedures allows a clearly defined
+and intuitive criterion for the object splits.
 
@@
 
-\noindent In \cite{Drelie08-298}, they have a partially annotated data set for segmentation of 
-histopathology images for nuclei segmentation.   However their study does not sollely focus on tripple negativ breast cancer patients and not only segmentation.
+Many traditional techniques have been proposed for the segmentation of
+nuclei in histopathology images, ranging from simple background
+subtraction and color threshold techniques\cite{Yuan2012} to much more
+sophisticated approaches, such as marked point
+processes\cite{Kulikova2012}. Many of these methods have been recently
+reviewed \cite{irshad2014methods}.
 
-%% fill in more information about that dataset
-
-Image segmentation and object recognition in medical imagining have 
-been tackled for many years and many approaches have been found. 
-Methods based on mathematical morphological operators have been 
-widely used and applied for segmentation and feature extraction, 
-however such methods rely on the user to manually define the 
-information that is relevant for his task \cite{irshad2014methods}. 
-Segmentation methods based on a strong priori information are also 
-possible and yield comparable results in terms of accuracy, in 
-\cite{ranefall2016fast} they segment the picture using mathematical 
-morphology with an ellispe fit condition 
-which is considerably faster than other state of the art methods. 
+%Image segmentation and object recognition in medical imaging have 
+%been tackled for many years and many approaches have been proposed. 
+%Methods based on mathematical morphology have been 
+%widely used and applied for segmentation and feature extraction, 
+%however such methods rely on the user to manually define the 
+%information that is relevant for his task \cite{irshad2014methods}. 
+%Segmentation methods based on a strong priori information are also 
+%possible and yield comparable results in terms of accuracy, in 
+%\cite{ranefall2016fast} they segment the picture using mathematical 
+%morphology with an ellispe fit condition 
+%which is considerably faster than other state of the art methods. 
 %Graph-
@@
 %then preprocessed to obtain the final segmentation.
+
 Alternative methods 
@@
 results that they achieved in the pascal voc challenge with 
-\cite{ImageNet}. Recent advances in deep neural network, and in 
+\cite{ImageNet}. Recent advances in deep neural networks, and in 
 particular in their optimization have made them become the state-of-the-
 art model for object recognition.  Deep neural network have also been 
-used for different task and have yielded very impressiv results, we can think of 
-semantic segmentation problems, where \cite{long2015fcn} use "de-
+used for 
+semantic segmentation, where \cite{long2015fcn} use "de-
 convolution layers" and up-sampling in order to identify and precisely 
@@
 
-\section{DataSet}
+Learning based methods rely on annotated data sets. But for the
+problem of nuclei segmentation in histopathology images, there are
+only few manually segmented images freely available. 
+In \cite{Drelie08-298}, a partially annotated data set has been
+released. However, this data set does not cover the morphological
+variability typically encountered in real histopathology data.
+
+\begin{figure}[htb]
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{RGB_1}}
+%  \vspace{1.5cm}
+  \centerline{Sample from patient 498959}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{GT_1}}
+%  \vspace{1.5cm}
+  \centerline{Associated ground truth}\medskip
+\end{minipage}
+%
+%
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{RGB_2}}
+%  \vspace{1.5cm}
+  \centerline{Sample from patient 581910}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{GT_2}}
+%  \vspace{1.5cm}
+  \centerline{Associated ground truth}\medskip
+\end{minipage}
+%
+%
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{RGB_3}}
+%  \vspace{1.5cm}
+  \centerline{Another one from patient 581910}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{GT_3}}
+%  \vspace{1.5cm}
+  \centerline{Associated ground truth}\medskip
+\end{minipage}
+%
+\caption{Random annotated samples from the dataset}
+\label{fig:annotation}
+%
+\end{figure}
+
+\section{Data set}
 \label{sec:dataset}
@@
 %% Contribution as a dataset, small introduction
-\noindent One of the main contributions of this paper is the now public available 
-nuclei detection dataset within HE stainned histopathology images which 
-can be found at website \url{http://cbio.mines-paristech.fr/~pnaylor/Downloads/HECellSegmentation.zip} 
+\noindent One of the contributions of this paper is the now publicly available 
+nuclei detection dataset within HE stained histopathology images which 
+can be found at \url{http://cbio.mines-paristech.fr/~pnaylor/Downloads/HECellSegmentation.zip} 
 (not a true address). This annotated dataset provides images clustered by 
 patients. Each patient has at least 3 annotated $512 \times 512$ HE 
-stainned histopathology images with their associated ground truth. Each 
-ground truth image is a $512 \times 512$ image where each pixel value above 
-$0$ is considered as a pixel belonging to a nuclei. The differences in 
-values of these pixels denote different nucleus, such an annotation can 
-be used in several processing step which does or doesn't take into 
-account clutered nuclei. See figure \ref{fig:annotation} for an example of 
+histopathology images with their associated ground truth. Each 
+ground truth image is a $512 \times 512$ label image where each pixel value above 
+$0$ is considered as the label of the corresponding nucleus. 
+See figure \ref{fig:annotation} for an example of 
 three annotated images. This annotation was conducted via the help of 
-the software ITK-snap, \cite{py06nimg} \url{http://www.itksnap.org}, and were annotated by the authors of the paper.
+the software ITK-snap, \cite{py06nimg} \url{http://www.itksnap.org} by
+the authors of this paper.
 
 %% Data set creation procedure
-These patients were randomly picked from an unpublished study on
-tripple negative breast cancer. For each of these patients we had access
-to their biopsy sample as a whole slide image (WSI). WSI enables a
-medical practitionner to digitize the huge amount of information that
-can be found in glass slides. WSI can be up to 60 GB big
-uncompressed and can't be stored in RAM on a standard computer. Given
-the WSI of a patient, we randomly cropped $512 \times 512$ samples 
+The patients were randomly picked from an unpublished study on
+triple negative breast cancer (TNBC). For each of the patients we had access
+to a biopsy and a whole slide image (WSI). WSI are very large images
+and can be up to 60 GB 
+(uncompressed). As they cannot be stored in the RAM of a standard computer, we randomly cropped $512 \times 512$ samples 
 from the WSI. %% explain that we choose the tissue area? 
-3 to 7 images were choosen from the randomly sampled images to try and give the most diversed dataset among these patients.
-Once the samples were choosen, we fully annotated each nuclei via the software ITK-snap and touching nuclei are differentiate via a different annotation value.
+3 to 7 images were choosen from the randomly sampled images to try and
+give the most diverse dataset among these patients. Once the samples
+were choosen, we fully annotated each nucleus via the software
+ITK-snap; touching nuclei were differentiated by the different label
+value.
 
@@
 %% I asked Marick's help for this paragraph!
-In this data set we have annotated a considerous amount of cells,
+In this data set we have annotated a considerable amount of cells,
 including normal epithelial and myoepithelial breast cells (localized in
@@
 cells, adipocytes, macrophages and
-inflammatory cells (lymphocytes and plasmocytes). For the moment, cell 
-types have not been included, which means that in this dataset every annotation corresponds to a global type: cell.
-We can also give some simple statistics with respect to the dataset.
-We have 33 images with a total of 2754 annotated cells, the maximum number of cells in one sample is 293 and the minimum number of cells in one sample is 5.
-We also have on average 83 cells per sample with a high standard deviation of 63.
+inflammatory cells (lymphocytes and plasmocytes). For the moment, we
+did not annotate the different cell types, however.
+
+In total, we have 33 images with a total of 2754 annotated cells,
+the maximum number of cells in one sample is 293 and the minimum
+number of cells in one sample is 5. We also have on average 83 cells
+per sample with a high standard deviation of 63.
 
@@
 We have our training set $(A_l,B_l)_{l \in [1, N]}$ where N is equal to 
-33, how ever each element $A_l$ belongs to a certain patients and 
+33, however each element $A_l$ belongs to a certain patients and 
 several elements $A_l$ can belong to the same patient. As we are 
-dealing with histopathology images, it is know that samples can widely 
+dealing with histopathology images, it is known that samples can widely 
 vary from one patient to the other. We thus validate our model by a 
-leave one patient out scheme. Our validation scheme is as followed, for a 
-given set of hype parameters, we 
+leave one patient out scheme. 
+For this reason we use a leave-one-patient-out strategy: for a 
+given set of hyper parameters, we 
 train our model on every patient except one that is used for validation. 
 Our final score is averaged over all patients.
-Several metrics assess the quality of the model, the accuracy, the 
-F1 score and a performance score which is the mean between the 
-true positive rate and the true negative rate.
+Several metrics give a detailed assessment of the model quality: accuracy, 
+F1 score and a performance score which is the mean between 
+true positive rate and true negative rate.
 
@@
 used a great number of transformation for the data augmentation. From 
-a original size of 33 annotated images, adding flips, rotations, bluriness 
+an original size of 33 annotated images, adding flips, rotations, bluriness 
 and random elastic deformations enabled us to have more then 
@@
 We therefore fixed the momentum to be 0.9 and the weight decay to be 
-$5.10^{-5}$ for all of the experiences, the learning rate was tunned 
-according to the model choosen.
-We also experienced with different 
-initialization value and if possible, we also considered pretrained layers. 
-Using pretrained layers made learning more efficient and made score 
-values more robust.
+$5.10^{-5}$ for all of the experiments, the learning rate was tuned 
+according to the model chosen.
+We also experimented with different 
+initialization values and if possible, we also considered pretrained layers. 
+The use of pretrained layers made learning more efficient and made scores 
+more robust.
 
@@
 The results obtained by the Deep Neural Network were encouraging, but
-touching nuclei were often segmented as one single object. This is not
-surprising, as the error at a pixel level seems very minor, and no
-shape prior is used in the model. Solving this issue by weighting the
+touching nuclei were often segmented as one single object. 
+%This is not
+%surprising, as the error at a pixel level seems very minor, and no
+%shape prior is used in the model. 
+Solving this issue by weighting the
 error term for pixels between objects did not solve the issue for our
@@
 nucleus border is systematically lower than in
-the putative center of the nucleus, but may still be larger than
-typically applied thresholds.This leads to the following rationale. As in the center of nuclei, the
+the putative center of the nucleus, but may still be relatively
+large. As in the center of nuclei, the
 posterior probability is maximal, we can readily assume that the local
@@
 larger than a parameter $\lambda$, we will perform a
-split. Conversely, if we can find a path that joins the two candidates
+split. Conversely, if we can find at least one path that joins the two candidates
 with a probability decrease smaller or equal to $\lambda$, no split
@@
 single object. Hence, the split is performed if: 
-\begin{equation}
+\begin{equation*}
 \min_{\mathcal{P}}C(\mathcal{P}) = \min_{\mathcal{P}} \{\max_{i=2
   \ldots N}{p_1-p_i}\} > \lambda
-\end{equation}
+\end{equation*}
 where $\lambda$ is a free parameter. This is actually nothing else
 than the morphological dynamics\cite{Grimaud1992}. The actual split
-locations are thus obtained by applying the watershed algorithm,
-starting from the local maxima of the posterior probability map with
-morphological dynamics larger than a free parameter $\lambda$.
+locations are then obtained by applying the watershed algorithm to the
+inverted posterior map,
+starting from the local minima with morphological dynamics larger than
+a free parameter $\lambda$. To speed up this procedure, we have developed an algorithm that
+performs selection and Watershed algorithm in a single pass by
+selectively building the Watershed line or fusing the regions.
 
-To speed up this procedure, we have developed an algorithm that
-performs selection and Watershed algorithm in a single pass by
-selectively building the Watershed line or fusing the regions,
-depending on the morphological dynamic at the moment at which two
-regions get in contact. This algorithm will be made publicly available
-through the open-source software scikit-image\cite{scikit-image}, in which we implemented
-all the steps which were not related to deep learning.
+\begin{figure}[htb]
+\begin{minipage}[b]{.48\linewidth}
+  \centering
+  \centerline{\includegraphics[height=4.0cm]{RGB_pred}}
+%  \vspace{1.5cm}
+  \centerline{Original RGB sample}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{0.48\linewidth}
+  \centering
+  \centerline{\includegraphics[width=4.0cm]{GT_pred}}
+%  \vspace{1.5cm}
+  \centerline{Associated ground truth}\medskip
+\end{minipage}
+
+\begin{minipage}[b]{0.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{BaochuanB}}
+%  \vspace{1.5cm}
+  \centerline{PangNet}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.5cm]{BaochuanP}}
+%  \vspace{1.5cm}
+  \centerline{Probability map}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{Baochuan_WS}}
+%  \vspace{1.5cm}
+  \centerline{Watershed}\medskip
+\end{minipage}
+
+%
+%
+\begin{minipage}[b]{0.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{DeconvNetB}}
+%  \vspace{1.5cm}
+  \centerline{DeconvNet}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{DeconvNetP}}
+%  \vspace{1.5cm}
+  \centerline{Probability map}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{DeconvNet_WS}}
+%  \vspace{1.5cm}
+  \centerline{Watershed}\medskip
+\end{minipage}
+%
+\begin{minipage}[b]{0.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{FCNB}}
+%  \vspace{1.5cm}
+  \centerline{FCN}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{FCNP}}
+%  \vspace{1.5cm}
+  \centerline{Probability map}\medskip
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.32\linewidth}
+  \centering
+  \centerline{\includegraphics[height=2.4cm]{FCN_WS}}
+%  \vspace{1.5cm}
+  \centerline{Watershed}\medskip
+\end{minipage}
+%
+\caption{Prediction via different classifiers of a random sample on the left out patient: 581910}
+\label{fig:prediction}
+%
+\end{figure}
+
+%depending on the morphological dynamic at the moment at which two
+%regions get in contact. 
+%This algorithm will be made publicly available
+%through the open-source software scikit-image\cite{scikit-image}, in which we implemented
+%all the steps which were not related to deep learning.
 
@@
 \label{sec:results}
-We experience with 3 known arhitectures in semantic segmentation, named PangNet, Fully Convolutionnal Net (FCN) and DeconvNet. The most basic architecture, PangNet, consists of 4 
-convolutionnal layer where each convolutionnal layer has 8 feature map, for more information please refer to \cite{pang2010cell}. 
+We experience with 3 known arhitectures in semantic segmentation,
+named PangNet, Fully Convolutionnal Net (FCN) and DeconvNet. The most
+basic architecture, PangNet, consists of 4  
+convolutional layers where each convolutional layer has 8 feature
+maps\cite{pang2010cell}.  
 This net, being not deep, has the advantage of being less 
@@
 feature" representations to the task of semantic segmentation. This 
-archicture has the advantage of re-using a classical deep learning 
-architecture with added on upsampling layer and skip layers. The 
+architecture has the advantage of re-using a classical deep learning 
+architecture with additional upsampling and skip layers. The 
 upsampling layers enable the network to learn a pixel level classification 
@@
 set of pretrained-weights extracted from the classical deep learning 
-architecture, for a more detailed explaination please refer to \cite{long2015fcn}. DeconvNet is also based on a classical architecture, 
-however, in this network their are no skip layer as one intends to learn 
-the proper upsampling threw repeated deconvolution and convolution 
-layers. This model can also be fine tuned, for more information please 
-refer to the original paper \cite{noh2015learning}. We also did an
+architecture\cite{long2015fcn}. DeconvNet is also based on a classical architecture, 
+however, in this network their are no skip layers as one intends to learn 
+the proper upsampling through repeated deconvolution and convolution 
+layers. This model can also be fine tuned\cite{noh2015learning}. We also did an
 ensemble classifier of these two previous nets as suggested in 
@@
 \cite{jia2014caffe}. We present our results in table \ref{tab:res} where 
-we averaged the metrics other all left out patients. We also added, for 
+we averaged the metrics over all left out patients. We also added, for 
 illustration purposes \ref{fig:prediction}, image predictions and 
@@
 We notice that the simpler net, PangNet seems to have learnt simple 
-rules such as color information. As we can not notice by the "holes" in 
-the probability map when the interior of the cell is very bright. On the 
+rules such as color information. As soon as the nuclei are not
+homogeneous and dark inside, the method fails ( "holes" in the
+cells). On the 
 contrary, deeper nets as FCN and DeconvNet have learnt deeper features 
@@
 the third 
-column. Our post-processing 
+column. By construction, our post-processing 
 scheme is very sensitive to noise as we can see in the PangNet 
@@
 the image, this value can be found by cross validation or by simple 
-visualation of the results.
+visualization of the results.
 \begin{table}
@@
 \label{sec:conclusion}
+
+We have presented a fully automized workflow for segmenting nuclei in
+histopathology images based on deep learning and mathematical
+morphology. We have also generated a manually curated segmentation
+data base, which we make publicly available. We believe that such a
+method can become very useful for the investigation of cellular
+phenotypes at a tissue level and their relation to disease.
 
@@
 % -------------------------------------------------------------------------
-\begin{figure}[htb]
-\begin{minipage}[b]{.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{RGB_1}}
-%  \vspace{1.5cm}
-  \centerline{Sample from patient 498959}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{GT_1}}
-%  \vspace{1.5cm}
-  \centerline{Associated ground truth}\medskip
-\end{minipage}
-%
-%
-\begin{minipage}[b]{.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{RGB_2}}
-%  \vspace{1.5cm}
-  \centerline{Sample from patient 581910}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{GT_2}}
-%  \vspace{1.5cm}
-  \centerline{Associated ground truth}\medskip
-\end{minipage}
-%
-%
-\begin{minipage}[b]{.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{RGB_3}}
-%  \vspace{1.5cm}
-  \centerline{Another one from patient 581910}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{GT_3}}
-%  \vspace{1.5cm}
-  \centerline{Associated ground truth}\medskip
-\end{minipage}
-%
-\caption{Random annotated samples from the dataset}
-\label{fig:annotation}
-%
-\end{figure}
-
-\begin{figure}[htb]
-\begin{minipage}[b]{.48\linewidth}
-  \centering
-  \centerline{\includegraphics[height=4.0cm]{RGB_pred}}
-%  \vspace{1.5cm}
-  \centerline{Original RGB sample}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{GT_pred}}
-%  \vspace{1.5cm}
-  \centerline{Associated ground truth}\medskip
-\end{minipage}
-
-\begin{minipage}[b]{0.32\linewidth}
-  \centering
-  \centerline{\includegraphics[height=2.4cm]{BaochuanB}}
-%  \vspace{1.5cm}
-  \centerline{PangNet}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{.32\linewidth}
-  \centering
-  \centerline{\includegraphics[height=2.5cm]{BaochuanP}}
-%  \vspace{1.5cm}
-  \centerline{Probability map}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{.32\linewidth}
-  \centering
-  \centerline{\includegraphics[height=2.4cm]{Baochuan_WS}}
-%  \vspace{1.5cm}
-  \centerline{Watershed}\medskip
-\end{minipage}
-
-%
-%
-\begin{minipage}[b]{0.32\linewidth}
-  \centering
-  \centerline{\includegraphics[height=2.4cm]{DeconvNetB}}
-%  \vspace{1.5cm}
-  \centerline{DeconvNet}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{.32\linewidth}
-  \centering
-  \centerline{\includegraphics[height=2.4cm]{DeconvNetP}}
-%  \vspace{1.5cm}
-  \centerline{Probability map}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{.32\linewidth}
-  \centering
-  \centerline{\includegraphics[height=2.4cm]{DeconvNet_WS}}
-%  \vspace{1.5cm}
-  \centerline{Watershed}\medskip
-\end{minipage}
-%
-\begin{minipage}[b]{0.32\linewidth}
-  \centering
-  \centerline{\includegraphics[height=2.4cm]{FCNB}}
-%  \vspace{1.5cm}
-  \centerline{FCN}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{.32\linewidth}
-  \centering
-  \centerline{\includegraphics[height=2.4cm]{FCNP}}
-%  \vspace{1.5cm}
-  \centerline{Probability map}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{.32\linewidth}
-  \centering
-  \centerline{\includegraphics[height=2.4cm]{FCN_WS}}
-%  \vspace{1.5cm}
-  \centerline{Watershed}\medskip
-\end{minipage}
-%
-\caption{Prediction via different classifiers of a random sample on the left out patient: 581910}
-\label{fig:prediction}
-%
-\end{figure}
 
@@
 % -------------------------------------------------------------------------
-\vfill
-\pagebreak
+%\vfill
+%\pagebreak
 

### 2016-11-07 Paper.tex
shorter introduction

@@
 \usepackage{hyperref}
-\usepackage{seqsplit}
 
@@
 \maketitle
-\vspace{-1cm}
+
 %
@@
 For these reasons, analysis of histopathology data has received much
-attention over the last years. While many approaches aim at
-automatically performing the task of a human pathologist (Computer
-Aided Diagnosis, CAD), we want to investigate the influence of
-biologically relevant features, such as phenotype distributions or
-heterogeneity measures from the tissue data on different clinical
-variables, such as resistance to treatment or relapse probability.
-One essential step is thus the segmentation of nuclei from tissue
-images,  in order to assign them a cell type or phenotypic label and
-to evaluate their spatial distribution.
+attention over the last years. In particular for approaches aiming at
+relating biologically relevant features (such as phenotype
+distributions or heterogeneity measures) to clinical variables,
+segmentation of nuclei from tissue images is essential.
+
+%While many approaches aim at
+%automatically performing the task of a human pathologist (Computer
+%Aided Diagnosis, CAD), we want to investigate the influence of
+%biologically relevant features, such as phenotype distributions or
+%heterogeneity measures from the tissue data on different clinical
+%variables, such as resistance to treatment or relapse probability.
+%One essential step is thus the segmentation of nuclei from tissue
+%images,  in order to assign them a cell type or phenotypic label and
+%to evaluate their spatial distribution.
 
@@
 \label{sec:results}
-We experience with 3 known arhitectures in semantic segmentation,
-named PangNet, Fully Convolutionnal Net (FCN) and DeconvNet. The most
-basic architecture, PangNet, consists of 4  
-convolutional layers where each convolutional layer has 8 feature
-maps\cite{pang2010cell}.  
+\noindent We experience with 3 known arhitectures in semantic segmentation, named PangNet, Fully Convolutionnal Net (FCN) and DeconvNet. The most basic architecture, PangNet, consists of 4 
+convolutionnal layer where each convolutionnal layer has 8 feature map, for more information please refer to \cite{pang2010cell}. 
 This net, being not deep, has the advantage of being less 
@@
 
-We have presented a fully automized workflow for segmenting nuclei in
+We presented a fully automized workflow for segmenting nuclei in
 histopathology images based on deep learning and mathematical
@@
 
+%\begin{minipage}[b]{0.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{BaochuanB}}
+%%  \vspace{1.5cm}
+%  \centerline{PangNet}\medskip
+%\end{minipage}
+%\hfill
+%\begin{minipage}[b]{.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.5cm]{BaochuanP}}
+%%  \vspace{1.5cm}
+%  \centerline{Probability map}\medskip
+%\end{minipage}
+%\hfill
+%\begin{minipage}[b]{.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{Baochuan_WS}}
+%%  \vspace{1.5cm}
+%  \centerline{Watershed}\medskip
+%\end{minipage}
+%
+%%
+%%
+%\begin{minipage}[b]{0.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{DeconvNetB}}
+%%  \vspace{1.5cm}
+%  \centerline{DeconvNet}\medskip
+%\end{minipage}
+%\hfill
+%\begin{minipage}[b]{.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{DeconvNetP}}
+%%  \vspace{1.5cm}
+%  \centerline{Probability map}\medskip
+%\end{minipage}
+%\hfill
+%\begin{minipage}[b]{.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{DeconvNet_WS}}
+%%  \vspace{1.5cm}
+%  \centerline{Watershed}\medskip
+%\end{minipage}
+%%
+%\begin{minipage}[b]{0.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{FCNB}}
+%%  \vspace{1.5cm}
+%  \centerline{FCN}\medskip
+%\end{minipage}
+%\hfill
+%\begin{minipage}[b]{.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{FCNP}}
+%%  \vspace{1.5cm}
+%  \centerline{Probability map}\medskip
+%\end{minipage}
+%\hfill
+%\begin{minipage}[b]{.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{FCN_WS}}
+%%  \vspace{1.5cm}
+%  \centerline{Watershed}\medskip
+%\end{minipage}
+%%
+%\begin{minipage}[b]{0.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{EnsembleB}}
+%%  \vspace{1.5cm}
+%  \centerline{Ensemble}\medskip
+%\end{minipage}
+%\hfill
+%\begin{minipage}[b]{.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{EnsembleP}}
+%%  \vspace{1.5cm}
+%  \centerline{Probability map}\medskip
+%\end{minipage}
+%\hfill
+%\begin{minipage}[b]{.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{Ensemble_WS}}
+%%  \vspace{1.5cm}
+%  \centerline{Watershed}\medskip
+%\end{minipage}
+%\caption{Prediction via different classifiers of a random sample on the left out patient: 581910}
+%\label{fig:prediction}
+%%
+%\end{figure}
+
 % To start a new column (but not a new page) and help balance the last-page

### 2016-11-08 Paper.tex
reducing

@@
 \usepackage[francais]{babel}
-\usepackage{hyperref}
-
+%\usepackage{hyperref}
+\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
 % Example definitions.
@@
 
-Many traditional techniques have been proposed for the segmentation of
+\noindent Many traditional techniques have been proposed for the segmentation of
 nuclei in histopathology images, ranging from simple background
-subtraction and color threshold techniques\cite{Yuan2012} to much more
+subtraction and color threshold techniques \cite{Yuan2012} 
+to much more
 sophisticated approaches, such as marked point
@@
 have arisen from the achieving Convolutional neural networks 
-\cite{lecun}, in particular strong incentive rose with the very impressive 
-results that they achieved in the pascal voc challenge with 
-\cite{ImageNet}. Recent advances in deep neural networks, and in 
+%\cite{lecun}, 
+%in particular strong incentive rose with the very impressive 
+%results that they achieved in the pascal voc challenge with 
+%\cite{ImageNet}. 
+Recent advances in deep neural networks, and in 
 particular in their optimization have made them become the state-of-the-
@@
 %
-\begin{minipage}[b]{.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{RGB_2}}
+%\begin{minipage}[b]{.48\linewidth}
+ % \centering
+%  \centerline{\includegraphics[width=4.0cm]{RGB_2}}
 %  \vspace{1.5cm}
-  \centerline{Sample from patient 581910}\medskip
-\end{minipage}
-\hfill
-\begin{minipage}[b]{0.48\linewidth}
-  \centering
-  \centerline{\includegraphics[width=4.0cm]{GT_2}}
+%  \centerline{Sample from patient 581910}\medskip
+%\end{minipage}
+%\hfill
+%\begin{minipage}[b]{0.48\linewidth}
+%  \centering
+%  \centerline{\includegraphics[width=4.0cm]{GT_2}}
 %  \vspace{1.5cm}
-  \centerline{Associated ground truth}\medskip
-\end{minipage}
+%  \centerline{Associated ground truth}\medskip
+%\end{minipage}
 %
@@
 nuclei detection dataset within HE stained histopathology images which 
-can be found at \url{http://cbio.mines-paristech.fr/~pnaylor/Downloads/HECellSegmentation.zip} 
+can be found at \url{http://cbio.mines-paristech.fr/~pnaylor/BNS.zip} 
 (not a true address). This annotated dataset provides images clustered by 
@@
   \centering
-  \centerline{\includegraphics[height=4.0cm]{RGB_pred}}
+  \centerline{\includegraphics[height=3.0cm]{RGB_pred}}
 %  \vspace{1.5cm}
@@
   \centering
-  \centerline{\includegraphics[width=4.0cm]{GT_pred}}
+  \centerline{\includegraphics[width=3.0cm]{GT_pred}}
 %  \vspace{1.5cm}
@@
 \end{minipage}
+
+%\begin{minipage}[b]{0.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{EnsembleB}}
+%%  \vspace{1.5cm}
+%  \centerline{Ensemble}\medskip
+%\end{minipage}
+%\hfill
+%\begin{minipage}[b]{.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{EnsembleP}}
+%%  \vspace{1.5cm}
+%  \centerline{Probability map}\medskip
+%\end{minipage}
+%\hfill
+%\begin{minipage}[b]{.32\linewidth}
+%  \centering
+%  \centerline{\includegraphics[height=2.4cm]{Ensemble_WS}}
+%%  \vspace{1.5cm}
+%  \centerline{Watershed}\medskip
+%\end{minipage}
+
 %
@@
 
-\section{Different architectures/Results}
+\section{Different architectures}
 \label{sec:results}
@@
 ensemble classifier of these two previous nets as suggested in 
-\cite{noh2015learning}.
-% The final architecture that we tried is the UNet. This network combines 
-%both contribution of the above networks, the UNet has a similar 
-%architecture to the DeconvNet with skip layers.
-\section{Result and discussion}
+\cite{noh2015learning} but did not include any illustration as the results of the FCN were better.
+
+\section{Results and discussion}
 \label{sec:result}
@@
 F1    &       0.742 &     0.856 & 0.866  & 0.863\\
-TP       &       0.744 &     0.856 & 0.855 & 0.876 \\
-TN      &       0.963 &     0.981 &  0.977 & 0.979\\
+% TP       &       0.744 &     0.856 & 0.855 & 0.876 \\
+% TN      &       0.963 &     0.981 &  0.977 & 0.979\\
 Performance    &       0.853 &     0.918 & 0.916 & 0.928\\
-Pixel error  &  0.063 &     0.032 & 0.042 & 0.032\\
+% Pixel error  &  0.063 &     0.032 & 0.042 & 0.032\\
 \hline
@@
 
-We presented a fully automized workflow for segmenting nuclei in
+\noindent We presented a fully automized workflow for segmenting nuclei in
 histopathology images based on deep learning and mathematical
@@
 phenotypes at a tissue level and their relation to disease.
-
-%I don't really know if we need something like this...
 
@@
 %\end{tabular}
-
-%\section{Formatting your paper}
-%\label{sec:format}
-%
-%All printed material, including text, illustrations, and charts, must be kept
-%within a print area of 7 inches (178 mm) wide by 9 inches (229 mm) high. Do
-%not write or print anything outside the print area. The top margin must be 1
-%inch (25 mm), except for the title page, and the left margin must be 0.75 inch
-%(19 mm).  All {\it text} must be in a two-column format. Columns are to be 3.39
-%inches (86 mm) wide, with a 0.24 inch (6 mm) space between them. Text must be
-%fully justified.
-%
-%\section{PAGE TITLE SECTION}
-%\label{sec:pagestyle}
-%
-%The paper title (on the first page) should begin 1.38 inches (35 mm) from the
-%top edge of the page, centered, completely capitalized, and in Times 14-point,
-%boldface type.  The authors' name(s) and affiliation(s) appear below the title
-%in capital and lower case letters.  Papers with multiple authors and
-%affiliations may require two or more lines for this information.
-%
-%\section{TYPE-STYLE AND FONTS}
-%\label{sec:typestyle}
-%
-%To achieve the best rendering both in the proceedings and from the CD-ROM, we
-%strongly encourage you to use Times-Roman font.  In addition, this will give
-%the proceedings a more uniform look.  Use a font that is no smaller than nine
-%point type throughout the paper, including figure captions.
-%
-%In nine point type font, capital letters are 2 mm high.  If you use the
-%smallest point size, there should be no more than 3.2 lines/cm (8 lines/inch)
-%vertically.  This is a minimum spacing; 2.75 lines/cm (7 lines/inch) will make
-%the paper much more readable.  Larger type sizes require correspondingly larger
-%vertical spacing.  Please do not double-space your paper.  True-Type 1 fonts
-%are preferred.
-%
-%The first paragraph in each section should not be indented, but all the
-%following paragraphs within the section should be indented as these paragraphs
-%demonstrate.
-%
-%\section{MAJOR HEADINGS}
-%\label{sec:majhead}
-%
-%Major headings, for example, "1. Introduction", should appear in all capital
-%letters, bold face if possible, centered in the column, with one blank line
-%before, and one blank line after. Use a period (".") after the heading number,
-%not a colon.
-%
-%\subsection{Subheadings}
-%\label{ssec:subhead}
-%
-%Subheadings should appear in lower case (initial word capitalized) in
-%boldface.  They should start at the left margin on a separate line.
-% 
-%\subsubsection{Sub-subheadings}
-%\label{sssec:subsubhead}
-%
-%Sub-subheadings, as in this paragraph, are discouraged. However, if you
-%must use them, they should appear in lower case (initial word
-%capitalized) and start at the left margin on a separate line, with paragraph
-%text beginning on the following line.  They should be in italics.
-%
-%\section{PRINTING YOUR PAPER}
-%\label{sec:print}
-%
-%Print your properly formatted text on high-quality, 8.5 x 11-inch white printer
-%paper. A4 paper is also acceptable, but please leave the extra 0.5 inch (12 mm)
-%empty at the BOTTOM of the page and follow the top and left margins as
-%specified.  If the last page of your paper is only partially filled, arrange
-%the columns so that they are evenly balanced if possible, rather than having
-%one long column.
-%
-%In \LaTeX, to start a new column (but not a new page) and help balance the
-%last-page column lengths, you can use the command ``$\backslash$pagebreak'' as
-%demonstrated on this page (see the \LaTeX\ source below).
-%
-%\section{PAGE NUMBERING}
-%\label{sec:page}
-%
-%Please do {\bf not} paginate your paper.  Page numbers, session numbers, and
-%conference identification will be inserted when the paper is included in the
-%proceedings.
-%
-%\section{ILLUSTRATIONS, GRAPHS, AND PHOTOGRAPHS}
-%\label{sec:illust}
-%
-%Illustrations must appear within the designated margins.  They may span the two
-%columns.  If possible, position illustrations at the top of columns, rather
-%than in the middle or at the bottom.  Caption and number every illustration.
-%All halftone illustrations must be clear black and white prints.  If you use
-%color, make sure that the color figures are clear when printed on a black-only
-%printer.
-%
-%Since there are many ways, often incompatible, of including images (e.g., with
-%experimental results) in a \LaTeX\ document, below is an example of how to do
-%this \cite{Lamp86}.
-
-% Below is an example of how to insert images. Delete the ``\vspace'' line,
-% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
-% with a suitable PostScript file name.
-% -------------------------------------------------------------------------
-
-%\begin{minipage}[b]{0.32\linewidth}
-%  \centering
-%  \centerline{\includegraphics[height=2.4cm]{BaochuanB}}
-%%  \vspace{1.5cm}
-%  \centerline{PangNet}\medskip
-%\end{minipage}
-%\hfill
-%\begin{minipage}[b]{.32\linewidth}
-%  \centering
-%  \centerline{\includegraphics[height=2.5cm]{BaochuanP}}
-%%  \vspace{1.5cm}
-%  \centerline{Probability map}\medskip
-%\end{minipage}
-%\hfill
-%\begin{minipage}[b]{.32\linewidth}
-%  \centering
-%  \centerline{\includegraphics[height=2.4cm]{Baochuan_WS}}
-%%  \vspace{1.5cm}
-%  \centerline{Watershed}\medskip
-%\end{minipage}
-%
-%%
-%%
-%\begin{minipage}[b]{0.32\linewidth}
-%  \centering
-%  \centerline{\includegraphics[height=2.4cm]{DeconvNetB}}
-%%  \vspace{1.5cm}
-%  \centerline{DeconvNet}\medskip
-%\end{minipage}
-%\hfill
-%\begin{minipage}[b]{.32\linewidth}
-%  \centering
-%  \centerline{\includegraphics[height=2.4cm]{DeconvNetP}}
-%%  \vspace{1.5cm}
-%  \centerline{Probability map}\medskip
-%\end{minipage}
-%\hfill
-%\begin{minipage}[b]{.32\linewidth}
-%  \centering
-%  \centerline{\includegraphics[height=2.4cm]{DeconvNet_WS}}
-%%  \vspace{1.5cm}
-%  \centerline{Watershed}\medskip
-%\end{minipage}
-%%
-%\begin{minipage}[b]{0.32\linewidth}
-%  \centering
-%  \centerline{\includegraphics[height=2.4cm]{FCNB}}
-%%  \vspace{1.5cm}
-%  \centerline{FCN}\medskip
-%\end{minipage}
-%\hfill
-%\begin{minipage}[b]{.32\linewidth}
-%  \centering
-%  \centerline{\includegraphics[height=2.4cm]{FCNP}}
-%%  \vspace{1.5cm}
-%  \centerline{Probability map}\medskip
-%\end{minipage}
-%\hfill
-%\begin{minipage}[b]{.32\linewidth}
-%  \centering
-%  \centerline{\includegraphics[height=2.4cm]{FCN_WS}}
-%%  \vspace{1.5cm}
-%  \centerline{Watershed}\medskip
-%\end{minipage}
-%%
-%\begin{minipage}[b]{0.32\linewidth}
-%  \centering
-%  \centerline{\includegraphics[height=2.4cm]{EnsembleB}}
-%%  \vspace{1.5cm}
-%  \centerline{Ensemble}\medskip
-%\end{minipage}
-%\hfill
-%\begin{minipage}[b]{.32\linewidth}
-%  \centering
-%  \centerline{\includegraphics[height=2.4cm]{EnsembleP}}
-%%  \vspace{1.5cm}
-%  \centerline{Probability map}\medskip
-%\end{minipage}
-%\hfill
-%\begin{minipage}[b]{.32\linewidth}
-%  \centering
-%  \centerline{\includegraphics[height=2.4cm]{Ensemble_WS}}
-%%  \vspace{1.5cm}
-%  \centerline{Watershed}\medskip
-%\end{minipage}
-%\caption{Prediction via different classifiers of a random sample on the left out patient: 581910}
-%\label{fig:prediction}
-%%
-%\end{figure}
-
-% To start a new column (but not a new page) and help balance the last-page
-% column length use \vfill\pagebreak.
-% -------------------------------------------------------------------------
-%\vfill
-%\pagebreak
-
-%\section{FOOTNOTES}
-%\label{sec:foot}
-%
-%Use footnotes sparingly (or not at all!) and place them at the bottom of the
-%column on the page on which they are referenced. Use Times 9-point type,
-%single-spaced. To help your readers, avoid using footnotes altogether and
-%include necessary peripheral observations in the text (within parentheses, if
-%you prefer, as in this sentence).
-%
-
-%\section{COPYRIGHT FORMS}
-%\label{sec:copyright}
-%
-%You must include your fully completed, signed IEEE copyright release form when
-%you submit your paper. We {\bf must} have this form before your paper can be
-%published in the proceedings.  The copyright form is available as a Word file,
-%a PDF file, and an HTML file. You can also use the form sent with your author
-%kit.
-
-%\section{REFERENCES}
-%\label{sec:ref}
-
-%List and number all bibliographical references at the end of the
-%paper.  The references can be numbered in alphabetic order or in
-%order of appearance in the document.  When referring to them in the
-%text, type the corresponding reference number in square brackets as
-%shown at the end of this sentence \cite{C2}.
-
-% References should be produced using the bibtex program from suitable
-% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
-% style file from IEEE produces unsorted bibliography list.
-% -------------------------------------------------------------------------
 \bibliographystyle{IEEEbib}

### 2016-11-08 Paper.tex
In 4

@@
 nuclei in histopathology images, ranging from simple background
-subtraction and color threshold techniques \cite{Yuan2012} 
+subtraction and color threshold techniques 
 to much more
@@
 Alternative methods 
-have arisen from the achieving Convolutional neural networks 
+have arisen from the achieving Convolutional neural networks.
 %\cite{lecun}, 

### 2017-01-18 Paper.tex
update of table
what changes

@@
 %  \vspace{1.5cm}
-  \centerline{Another one from patient 581910}\medskip
+  \centerline{Sample from patient 581910}\medskip
 \end{minipage}
@@
 nuclei detection dataset within HE stained histopathology images which 
-can be found at \url{http://cbio.mines-paristech.fr/~pnaylor/BNS.zip} 
-(not a true address). This annotated dataset provides images clustered by 
+can be found at \url{http://cbio.mines-paristech.fr/~pnaylor/BNS.zip}. This annotated dataset provides images clustered by 
 patients. Each patient has at least 3 annotated $512 \times 512$ HE 
@@
 Our final score is averaged over all patients.
-Several metrics give a detailed assessment of the model quality: accuracy, 
+Several metrics give a detailed assessment of the model quality: accuracy, intersection over union (IU),
 F1 score and a performance score which is the mean between 
@@
 We picked $\lambda = 7$ which seemed to give a nice partitionning of 
-the image, this value can be found by cross validation or by simple 
-visualization of the results.
+the image, this value can be found by cross validation.
 \begin{table}

### 2017-01-20 Paper.tex
updated
et al

@@
 variability typically encountered in real histopathology data.
+Moreover, nuclei spot detection in histopathology has been tackled in breast and colon cancer in \cite{xu2016stacked} and \cite{sirinukunwattana2016locality}.
+Our setup is different in terms of architecture as we use a very deep architecture for segmentation and not image patches for nuclei centroid detection.
 
@@
 
+\vspace{-1cm}
 \section{Different architectures}
@@
 ensemble classifier of these two previous nets as suggested in 
-\cite{noh2015learning} but did not include any illustration as the results of the FCN were better.
-
+\cite{noh2015learning} but did not include any illustration. Processing 
+one image of size $224 \times 224$ pixels took on average 0.91 secondes for 
+PangNet, which is the smallest network, and it took on average 3.38 secondes for DeconvNet, the 
+largest network. These times do not depend on the number of cells. These computation 
+times were estimated on a K620 Quadro graphics card.
+\vspace{-0.3cm}
 \section{Results and discussion}
@@
  \hline
-Accuracy  &       0.936 & 0.968 &0.958 & 0.968  \\
-IU   &    0.759 &     0.856 & 0.857 & 0.861 \\
-Recall     &       0.744  &     0.856 & 0.855 & 0.876\\
-Precision   &       0.741 &     0.858 & 0.878 & 0.851\\
-F1    &       0.742 &     0.856 & 0.866  & 0.863\\
+Accuracy  &  0.924 & 0.954 &0.944 & 0.944  \\
+IU   &    0.722 &  0.814 & 0.782 & 0.804 \\
+Recall     &  0.655  & 0.773 & 0.752 & 0.900 \\
+Precision   &  0.814 & 0.864 & 0.823 & 0.741 \\
+F1    &       0.676 &     0.805 & 0.763  & 0.802\\
 % TP       &       0.744 &     0.856 & 0.855 & 0.876 \\
 % TN      &       0.963 &     0.981 &  0.977 & 0.979\\
-Performance    &       0.853 &     0.918 & 0.916 & 0.928\\
+Performance    &   0.803   & 0.875 & 0.862 & 0.922 \\
 % Pixel error  &  0.063 &     0.032 & 0.042 & 0.032\\

### 2017-01-20 Paper.tex
shortened to 4 pages

@@
 sophisticated approaches, such as marked point
-processes\cite{Kulikova2012}. Many of these methods have been recently
+processes. Many of these methods have been recently
 reviewed \cite{irshad2014methods}.
@@
 
-Alternative methods 
-have arisen from the achieving Convolutional neural networks.
+%Alternative methods 
+%have arisen from the achieving Convolutional neural networks.
 %\cite{lecun}, 
@@
 %\cite{ImageNet}. 
-Recent advances in deep neural networks, and in 
+More recently, advances in deep convolutional neural networks (CNN), and in 
 particular in their optimization have made them become the state-of-the-
-art model for object recognition.  Deep neural network have also been 
-used for 
-semantic segmentation, where \cite{long2015fcn} use "de-
-convolution layers" and up-sampling in order to identify and precisely 
-locate objects within a picture. Different architecture arising from 
-different intuition are also possible and have been applied in this paper.
+art model for object recognition. 
+Indeed, deep neural networks have been used for the localization and classification of nuclei in histopathology data from breast and colon cancer \cite{xu2016stacked,sirinukunwattana2016locality}, but these previously published approaches do no allow for segmentation.
+
+On the other hand, deep CNN have also been used for semantic segmentation in other fields, where \cite{long2015fcn} use "de-convolution layers" and up-sampling in order to directly output binary images.
+The rationale of our proposed method was therefore to learn segmentation directly from annotated samples with this or similar architectures.
+
+%identify and precisely 
+%locate objects within a picture. Different architectures arising from 
+%different intuition are also possible and have been applied in this paper.
 
@@
 variability typically encountered in real histopathology data.
-Moreover, nuclei spot detection in histopathology has been tackled in breast and colon cancer in \cite{xu2016stacked} and \cite{sirinukunwattana2016locality}.
-Our setup is different in terms of architecture as we use a very deep architecture for segmentation and not image patches for nuclei centroid detection.
 
@@
 %  \vspace{1.5cm}
-  \centerline{Sample from patient 498959}\medskip
+%  \centerline{Sample from patient 498959}\medskip
+  \centerline{Sample from patient 1}\medskip
 \end{minipage}
@@
 %  \vspace{1.5cm}
-  \centerline{Sample from patient 581910}\medskip
+ % \centerline{Sample from patient 581910}\medskip
+  \centerline{Sample from patient 2}\medskip
 \end{minipage}
@@
 We have our training set $(A_l,B_l)_{l \in [1, N]}$ where N is equal to 
-33, however each element $A_l$ belongs to a certain patients and 
+33, however each element $A_l$ belongs to a certain patient and 
 several elements $A_l$ can belong to the same patient. As we are 
@@
 vary from one patient to the other. We thus validate our model by a 
-leave one patient out scheme. 
-For this reason we use a leave-one-patient-out strategy: for a 
+leave-one-patient-out scheme: for a 
 given set of hyper parameters, we 
@@
 %
-\caption{Prediction via different classifiers of a random sample on the left out patient: 581910}
+\caption{Prediction via different classifiers of a random sample on the (same) left out patient}
 \label{fig:prediction}
@@
 
-\vspace{-1cm}
+%\vspace{-.2cm}
 \section{Different architectures}
@@
 and seem capable of recognizing whole cells. On these probability maps 
-we applied our watershed segmentation and we can picture the results in 
+we applied our postprocessing scheme and we can picture the results in 
 the third 
-column. By construction, our post-processing 
-scheme is very sensitive to noise as we can see in the PangNet 
-prediction, many unrelated minimas will lead to highly partitionned cell. 
+column. By construction, the postprocessing relies on a smooth posterior probability as we can see in the PangNet 
+prediction: many unrelated minimas will lead to oversegmentation. 
 This phenomenom also appears with the DeconvNet where undesired 
@@
 We picked $\lambda = 7$ which seemed to give a nice partitionning of 
-the image, this value can be found by cross validation.
+the image, this value can also be found by cross validation.
 \begin{table}
